\section{The First Turnabout}
The party enters Losokyo expecting to meet \linkto{people:miafey}, however they are met by \linkto{tbd}, who welcomes them and informs the party that Mia is busy and so they were asked to show them around. TBD guides them to the center of the city, pointing out the central Court House and the clock tower at the top. 
\begin{center}
``It truly is a wonderful chime. I've lived here for nigh on a decade and still enjoy its song every hour.''
- TBD \end{center}

After answering any questions the party may have about the city, TBD then directs them towards the Gatewater Hotel, where rooms have already been reserved for the party. Shortly after entering, however, TBD leaves the party to exit the hotel in order to hear the 2PM chime of the clock tower, inviting the party out to hear it.

\begin{center}
``This hotel is special; you can't hear the clock tower from inside. I figure they don't want it disturbing the guests if they're trying to nap midday or something. This hotel serves plenty of foreign tourists, who may suffer from tele-lag. Similarly, the rooms are entirely sound-proof.''
\end{center}

Upon re-entering the hotel, \linkto{people:larry} walks by, possibly unnoticed. If noticed, he is clearly annoyed and unwilling to talk to anyone. TBD then leads the party to their room, a suite with N bedrooms on the side of a large meeting room on the fourth floor. There is a balcony, which looks over Fey \& Co. Law Offices. When the lighting is right (say, at night), you can see right through the window into the main office. TBD answers any questions the party has about the accomodations and the city, and further informs them that Mia needed to defend a client in court on a very short notice, and so won't be available until later tonight.

About two hours later, if the party is in a public place, Detective \linkto{people:gumshoe} and the Losokyan police will arrive and arrest one of the party members (that looks like Larry\footnote{Setting this PC up to constantly be referred to as ``Harry Butz'' for the next week or so} for murder, and take that member to the Detention Center, and the trial will be tomorrow. Alternatively, if Larry is a close friend of any of the party members, he will be arrested instead. If the party figures out the crime scene and attempts to investigate it, they will mostly be stonewalled, as they are not lawyers and thus aren't allowed to investigate. However they might learn the following information from talking to Detective Gumshoe:
\begin{itemize}
\item The victim's name was Cindy Stone
\item Cindy was murdered via blunt force trauma
\item Cindy had just returned from Babahl
\end{itemize}
In particular, if the party asks anyone about Babahl, they should mention the need to change clocks.
\begin{center}
``Babahl? I've heard that place is wonderful, really well suited for tourists. There's just one annoyance, which is that it's so far away you have to adjust your clocks like nine hours ahead. Really messes with your system, you know?''
\end{center}

If the party goes to the detention center and the suspect is Larry, he will be confused. Earlier that day he went to Gatewater Hotel to visit his girlfriend, but she wasn't home, so he left and wandered around for the rest of the day. If pressed, he will say his girlfriend's name is Cindy Stone. If he finds out that Cindy Stone was murdered, he goes insane, blabbering about how his life is over, nothing matters anymore, he might as well get a guilty verdict, etc. 

\begin{center}
``Oh, it's all over... I... I'm finished. Finished! I can't live in a world without her! I can't! Who... who took her away from me? Who did this!? Aww, ya gotta tell me! Who took my baby away!?''
\end{center}

At some point, the party will be asked who will be defending the suspect. The only acceptable answer is for the party themselves (or a subset thereof) to do the defense, as they will not be able to meet with Mia before the deadline, and no lawyers they may find will be willing to take on a client with such short notice.

That night, Mia will visit the party and tell them she heard about what happened (if the suspect is not Larry), and asks if they managed to find a lawyer. Since the party has already registered themselves as the defense, Mia won't be able to be the attorney, however she will offer to stand at the bench as an assistant. 

\subsection{Trial}
The trial begins at 10 AM, although the group and the defendant meet in Defendant Lobby No. 2 to prepare for the case. If Larry was not the culprit, the bailiff will approach the party and inform them that due to new, conclusive evidence, the suspect in this case is now Larry Butz. Larry pleads with the party to save him, and Mia encourages the party to continue the defense, as he doesn't seem guilty. Once they have agreed, however, Larry will become incoherent, and the group continues discussing the case until the trial begins. Either Mia or the Bailiff will bring the party \linkto{evidence:cindyautopsy}. In the Courtroom, the \linkto{people:judge} will note that the defense team is new, and give a short test to ascertain their readiness:
\begin{itemize}
\item Please state the name of the defendant in this case. (If multiple choice: Party Member, Larry Butz, Mia Fey)
\item This is a murder trial; tell me, what wsa the victim's name? (If multiple choice: Mia Fey, Cinder Block, Cindy Stone)
\item What was the cause of death? She died because she was... (If multiple choice: Poisoned, hit with a blunt object, strangled)
\end{itemize}

The Judge then invites the prosecutor, \linkto{people:wpayne}, to explain what the murder weapon was: \linkto{evidence:thinker}, found lying on the floor, next to the victim. The prosecutor then calls Larry to the stand and asks some questions.

\subsubsection{Witness Testimony: Larry Butz}
\begin{center}
\begin{tabular}{p{2.5in} p{2.5in}}
Mr. Payne & Larry \\\hline
Ahem, Mr. Butz. Is it not true that the victim had recently dumped you? & Hey, watch it buddy! We were great together! We were Romeo and Juliet, Cleopatra and Mark Anthony! I wasn't dumped! She just wasn't responding to any of my letters! Or seeing me.. Ever. WHAT'S IT TO YOU, ANYWAY!? (continue from transcript, until ``Duuude!'')\\
We can clearly see what kind of woman this Ms. Stone was. Tell me, Mr. Butz, what do you think of her now? \\
\end{tabular}
\end{center}

At this point, Mia turns to the party and tells them that it would probably not be good to let Larry answer that question, although whether the party lets him or not, he will. Additionally, during that line of questioning, Payne will introduce the victim's \linkto{evidence:passport}, as evidence the victim went to Babahl.


\begin{center}
\begin{tabular}{p{2.5in} p{2.5in}}
Mr. Payne & Larry \\\hline
I believe the accused's motive is clear to everyone. Next queston! You went to the victim's apartment on the day of the murder, did you not? & Heh? Heh heh. Well, maybe I did, and maybe I didn't!
\end{tabular}
\end{center}

The Judge turns to the party, asking them to advise their client to answer the question. Regardless of whether they do, Mr. Payne interjects that he has a witness proving Larry did go to the victim's apartment that day. 

\begin{center}
``On the day of the murder, my witness was selling newspapers at the victim's building. Please bring Mr. Frank Sahwit to the stand!''
\end{center}

\subsubsection{Witness Testimony: Frank Sahwit 1}
\begin{center}
\begin{tabular}{p{4in}}
I was going door-to-door, selling subscriptions when I saw a man fleeing an apartment.\\
I thought he must be in a hurry because he left the door half-open behind him. \\
Thinking it strange, I looked inside the apartment. Then I saw her lying there... A woman... not moving... dead! \\
I quailed in fright and found myself unable to go inside. \\
I left to notify the police immediately! \\
I went to a nearby park and found a patrolling officer. \\
I remember the time exactly: It was 11:00 AM. \\
The man who ran was, without a doubt, the defendant sitting right over there. \\
\end{tabular}
\end{center}

Once the statement is over, the Judge asks Mr. Payne why the witness had to go all the way to a park to find a police officer, to which Mr. Payne informs the Judge that the same enchantments used to mute the clock tower occasionally disrupt police communications, and so they prefer not to patrol near the hotel. Satisfied, the Judge allows the party to begin their cross-examination. Mia, excited, tells the party that this is their chance to expose the lies in the witness's statement, and gives an introduction to the courtroom mechanics.

\begin{center}
``First, find contradictions between the evidence and the witness's testimony. Then, once you've found the contradicting evidence... present it and rub it in the witness's face!''
\end{center}

The contradiction is between the reported time (11:00 AM) and the time of death in the autopsy report (around 2-3 PM). While Payne tries to claim that the witness merely forgot the time, the Judge disagrees that that was possible, given how certain Sahwit was. After some discussion, Sahwit realizes what happens and asks to give further testimony.

\subsubsection{Witness Testimony: Frank Sahwit 2}
\begin{center}
\begin{tabular}{p{4in}}
You see, when I found the body, I heard the time. \\
There was a voice saying the time... It was probably coming from a neighboring room \\
Oh, but it was three hours off, wasn't it? \\
I guess the neighbors must have been discussing the past! \\
That's why I thought it was 11:00 AM! \\
Terribly sorry about the misunderstanding...
\end{tabular}
\end{center}

The contradiction is that rooms at the Gatewater Hotel are soundproof, and so it was impossible for someone to have heard a conversation coming from another room. Sahwit, increasingly agitated, comes up with another explanation, although the Judge is starting to become frustrated with the frequent corrections. \\

\subsubsection{Witness Testimony: Frank Sahwit 3}
\begin{center}
\begin{tabular}{p{4in}}
Actually, I didn't ``hear'' the time... I ``saw'' it!\\
There was a table clock in the apartment, wasn't there!\\
Yeah, the murder weapon! The killer used it to hit the victim!\\
That must have been what I saw. \\
\end{tabular}\end{center}

The contradiction is that the murder weapon was a statue, not a clock. Sahwit is starting to get angry and defensive now,\\
\begin{center}
``Whaa!? Y-you with your ``objections'', and your ``evidence''... Just who do you think you are!? Hey, I... I saw it there okay! That's a clock!''
\end{center}
At this point, Payne interrupts and informs the court that the statue is in fact a clock, that tells the time out loud when its neck is turned. However, since it looks like a statue, he submitted it as a statue. This, however, does not clarify how Sahwit knew it was a clock. The only reasonable explanation is that Sahwit went inside the apartment, and thus is likely the murderer. Sahwit is now almost incomprehensible.\\
\begin{center}
``I... I...! That... that day... I... I never! Look... I... the clock... I heard, no! I mean, I saw...Saw...nggg! Gwaaaaaah! Shutupshutupshutup! I hate you! I-it was him, I tell you! I saw him! H-he killed her and he should burn! Burn! Give him death!''\end{center}
After a moment of shock after his outburst, Payne steps up, flustered, pleading with the Judge not to be hasty, as there is not any evidence supporting the defense's claims. In response, the Judge asks the defense if they have any evidence that the sound the witness heard came from the clock. The only allowed response is to sound the clock; other options either have Mia butt in and explain why that is a bad idea, or the Judge will explain and penalize the party. \\
\begin{center}
``...*beep*...\textit{I think it's 8:25}''
\end{center}
The current time, of course, is 11:25. While this seems incriminating, Sahwit objects, saying that it proves nothing, as you have no way of showing that the clock was running slow on the day of the murder. The Judge, concurring, says that due to the lack of evidence, the cross-examination of Mr. Sahwit is over. If the party doesn't realize that they can prove the clock was running slow because it is still running on Babahlese time, Mia will object.
\begin{center}
``Don't waste time doubting the facts. Assume the clock was three hours slow and... Think through it! Ask yourself, `Why was the clock three hours slow?' Figure out the reason, and you'll have your proof! Right? Can you think of a reason as to why the clock would be three hours slow?''\end{center}
Satisfied, the Judge orders the arrest of Mr. Sahwit, and compliments the defense on such a quick case and on finding the true culprit. After some more possible pleasantries, he delivers his verdict: Not Guilty. 

\subsection{Post-Trial}

Mia congratulates the team on a job well done, but the cheery mood is spoiled by Larry's moping about his dead girlfriend. Mia congratulates ``Harry'', and after some conversation, gives a \linkto{items:thinker} to both Mia and to the party, although the one for the party looks a little wonky. He made three; one for Cindy and one for him, and one for practice. He then comments that he can't believe Cindy was playing him for a fool, that he was just another of her men. Mia disagrees, saying that she thinks that Cindy actually did have feelings for him, and prompts the party to explain what she's talking about. She is referring to the Thinker Statue, which Cindy took with her to Babahl, despite its bulk. If the party gives the wrong explanation, Larry will see through it, but in either case thank everyone and walk off. 

\begin{center}
``I hope you see the importance of evidence now. Also, hopefully you realize, things change depending on how you look at them. People, too. We never really know if our clients are guilty or innocent. All we can do is believe in them. And in order to believe in them, you have to believe in yourself. Listen. Learn. Grow strong. Never let go of what you believe in. Never.''\end{center}

Mia then will invite the party to dinner on her, toasting to ``an innocent Butz''.
\qed

\subsection{Evidence}
\subsubsection{Cindy's Autopsy Report}
\label{evidence:cindyautopsy}
Time of death: 2-3 PM, Ket 21. Cause of death: loss of blood due to blunt force trauma. 


\subsubsection{Thinker Statue}
\label{evidence:thinker}
A statue in the shape of ``The Thinker''. It's rather heavy. See \linkto{items:thinker}.

\subsubsection{Passport}
\label{evidence:passport}
Cindy Stone apparently returned from Babahl on Ket 20, the day before the murder. 