\section{Turnabout Memories}

Mia Fey's second trial, in which Arcadia Wright is accused of murdering Dee Swallow. 

\subsection{Pre-Trial}

Meet with Mr. Grossberg and Arcadia, introduce that Arcadia is sick with a cold. In a sort of internal-monologue way, introduce how court cases should be run.

\subsection{Start of the trial}
The trial begins with Prosecutor Payne making his opening statement and introducing Crime Photo 1 to the court. The Judge notes that he can't tell the cause of death, and Payne condescendingly allows Mia to answer, with Grossberg assisting if necessary.\\
\\
\begin{center}
Judge: Electrocution? Hmm... But how could such a thing happen? Did the murderer wear a super-heavy fur coat and rub their feet on the ground, perhaps?\\
Payne: The answer to that will become crystal clear as this trial proceeds, Your Honor. But before that, there is one more vital issue: the motive. Apparently there was some bad blood between the victim and the defendant. I'm sure the defense attorney would be more than happy to fill us in?\\
...\\
Payne: The prosecution would like to call Ms. Arcadia Wright as their first witness. \\
\end{center}

\subsection{The Victim and I}
Arcadia takes the stand, and after a sneeze- and cough- filled defense of their innocence, is invited to give testimony:\\
\begin{tabular}{c}
Um, I... I admit I was there... \\\hline
But I'm not a killer! All I did was find his body!\\\hline
I hardly knew the girl to begin with...\\\hline
I never even talked to that stuck-up Babahlese wannabe! \\\hline
\end{tabular}\\
\\
Asking how Arcadia knew Dee was a Babahlese wannabe yields a new line of testimony:\\
\begin{center}
He was always walking around with a huge Hato on the back of his shirt
\end{center}
The Hato is the national symbol of Babahl, a butterfly. This statement, however, contradicts Crime Photo 1. Mia points out that Arcadia was lying about not knowing Dee, and takes it somewhat personally. Payne thanks the defense for their work, and then asks Arcadia if they are taking any medicine. This conversation leads to Payne introducing Crime Photo 2, showing Dee holding Arcadia's Coldkiller X, as well as introducing the medicine itself. In response, Arcadia offers new testimony:

\subsection{What Really Happened}
\begin{tabular}{c}
The truth is... I went because she called me.\\\hline
She was in the Pharmacology Dept., so we agreed to meet at 2:45 behind that building...\\\hline
We talked for a bit, and then at around 3:00, we split up. \\\hline
Then later when I went back, I found him lying there. \\\hline
I'd been taking Coldkiller X for the last 2 or 3 days...\\\hline
But I lost my bottle of it around lunchtime on the day of the accident. \\\hline
\end{tabular}\\\\
Mia needs to ask more about the Pharmacology Department, which will result in the following statement:\\
\begin{center}
They have laboratories filled with chemicals and strange machines that run on electricity.
\end{center}
Pressing about the electricity,
\begin{center}
Getting the electricity to the labs isn't easy, they have to use these heavy-duty cables everywhere. There are poles that carry them set up all around the building.
\end{center}

Additionally, Mia needs to ask about what happened for lunch.
\begin{center}
I always eat with Dollie... Just the two of us. Dollie's homemade lunches are just the greatest! Mmm! Her mini-omelettes are magically delicious! Eheh heh heh.
\end{center}
This display causes Mia to stomp on Grossberg's foot.\\
\\
Once that has been done, the Judge will interject and say that while some facts of the case have been settled, it is clear that Arcadia's testimony cannot be trusted. The Judge then asks if the prosecution can explain how the murder was carried out, however Payne does not have an answer. Mia then sees a chance to improve her position by answering this question, and pointing out the cables in Crime Photo 1. \\
\\
Payne, however, is unfazed, as he claims that Arcadia is the only one who could have used the cables to murder Dee. Further, he adds that Arcadia's palm print was found on the front of Dee's leather jacket. With the Judge ready to deliver a verdict, Mia pleads with Arcadia to tell the truth, and she finally does:\\
\begin{tabular}{l}
Dee: That girl... You shouldn't see her anymore.\\
Arcadia: Hey! It's none of your business! \\
Dee: I'm telling you for your sake. If you continue to see her, it's going to be bad news. \\
Arcadia: Y-You're lying!\\
Dee: Just listen to me. There's something you need to know about that girl...\\
Arcadia: Stop it! D-Don't talk about her like that!\end{tabular}\\
Shocked by this outburst, the Judge allows Arcadia to make another testimony.

\subsection{When I Pushed the Victim}
\begin{tabular}{c}
That girl... She was talking bad about Dollie... \\\hline
I lost my temper and gave her a shove!\\\hline
At that moment, I heard some kind of loud noise...\\\hline
A little while after I left, I started to get worried.\\\hline
So I went back. But sh-she was just laying there, d-dead!\\\hline
\end{tabular}\\

Before the start of the cross-examination, Payne interjects that the simple explanation is that Ms. Swallow flew back and touched the electrical cable, an electrocution aided by the light rain that was falling. However, if Mia asks about the loud noise, Payne will first answer that it was the sound of the victim being electrocuted, but if she presses harder, Arcadia will remember that it was Dee's umbrella that snapped when she fell on top of it. She, when prompted, will ask Arcadia to add that statement to her testimony:
\begin{center}
After I shoved her, she... She fell down on top of her cheap umbrella
\end{center}
This contradicts the crime photo, as it the umbrella should have been stuck under Dee's body. The Judge is not overly impressed with this contradiction, but agrees it is enough to prevent a verdict. The umbrella and Arcadia's testimony are added to the Court Record. However, Payne will comment that while he was hoping to establish his case through cross-examination alone, he does have another witness: Ms. Dahlia Hawthorne. In preparation, the court takes a 20 minute recess.

\subsection{The Recess}
Arcadia is relieved that Dollie will be testifying, as she believes she will clear her name. Mia is not impressed, and asks how Arcadia and Dahlia met:
\begin{center}
 Dollie and I... We first met about eight months ago right here in this very courthouse. Actually, I'm studying to be a lawyer, on the side... Anyway! One day, she and I just bumped into each other in the reading room downstairs. That's why I really think it was fate that brought us together. As soon as I first set eyes on her, I knew she was the one for me. Oh, here! Take a look at this! (shows necklace) She gave this to me the day we met as a symbol of our love! She had been wearing it around her neck that day, but then... ...she took it off, but before she gave it to me she said, "I want you to carry this."
 \end{center}
 
Arcadia will also comment that every time they meet, she asks for it back, which he sees as some cutsey move and not an earnest request. Mia then asks if the day they met was Neige 27, which it was, and she shows him a newspaper clipping (which is then added to the court record). Grossberg suddenly understands Mia's interest in this case, and decides to investigate in the reading room for more information.

\subsection{What I Witnessed}
After reconvening, Mr. Payne calls Dahlia to the stand. He and the Judge are completely enthralled by her, and it is Mia that coolly asks for her name and occupation. At first, she tries to defend Arcadia
\begin{center}
I'm sure that there must be some kind of mistake. Daisy wouldn't kill anyone. I just know it!
\end{center}
She then proceeds to her testimony:\\
\begin{tabular}{c}
I had been planning to go back to Daisy's place after class was over. \\\hline
Daisy and Dee-gal... They were talking behind the building. \\\hline
Then suddenly... Dee-gal got all wobbly and just collapsed. \\\hline
That's when Daisy noticed that I was there. \\\hline
I went to go and find some other students and they called the authorities. \\\hline
\end{tabular}\\

While this testimony appears to help Mia, she refuses to win a case based on lies, prompting a back-and-forth with Dahlia. In any case, Mia points out that the testimony is missing the part where Arcadia pushed the victim. To this, the third and fourth statements change:
\begin{center}
Um, actually, I didn't see the moment she pushed Dee-gal\\
It didn't look like they were fighting, and I didn't hear any noise either
\end{center}

This introduces an obvious contradiction with Arcadia's testimony. However, Dahlia claims that she didn't hear the noise because it was thundering and so she had earplugs in. Mia seizes this opportunity to claim that Dee was hit by a bolt of lightning, however Payne counters that there were actually no lightning strikes in that part of the city that day, and also that they have testimony from one of the Pharmacology students that all equipment lost power suddenly around 3 PM that day. Apparently, the cables were very brittle, so even the smallest bump would've caused them to break. \\
\\
The Judge mulls over this, and realizes the contrapositive: if there was no bump, then the cable would not have snapped. He then turns to Mia and asks if she has an idea of what caused the cable to break. While she admits it was Arcadia's shove, she points out that if Dee was pushed and landed where the umbrella is, then she couldn't have been electrocuted by the cables across the way. \\
\\
Dahlia then interjects, claiming that she remembers things a little differently, and is asked to give more testimony.

\subsection{What I Witnessed, Pt 2}
\begin{tabular}{c}
The truth is... Daisy pushed her twice. \\\hline
The first time was into the electrical pole. That's when the cable broke. \\\hline
Then Dee-gal tried her best to run away from her... \\\hline
But Daisy caught up and crashed into her from behind. \\\hline
The cable snapping, and Dee-gal being electrocuted -- it all occured in less than a minute. \\\hline
\end{tabular}\\
\\
Mia points out the obvious contradiction with the timing, and claims that the real murderer committed the crime during the 10 minute gap. When asked who the real murderer is, she identifies Dahlia Hawthorne. To back up her claim, she asks Dahlia to testify about how she and Arcadia met.

\subsection{How I Met My Daisy}
\begin{tabular}{c}
I first met my darling Daisy eight months ago.\\\hline
It's like we were destined to meet in this very courthouse's basement reading room.\\\hline
The moment our eyes met, my heart skipped a beat!\\\hline
We've been going out ever since that fateful day.\\\hline
\end{tabular}\\
Arcadia then chimes in right afterwards
\begin{center}
We're so lovey-wuvey we literally make people sick! It's just jealousy, I think...
\end{center}
She is swiftly reprimanded by the Judge, however. In any case, Mia questions Dahlia as to why she was in the reading room, to which she responds\\
\begin{center}
I had come to this courthouse to do some research for a paper I was writing
\end{center}
Mia argues that this is not true, and that Dahlia actually came to the courthouse to commit the murder that she became a suspect in, as evidenced in the Police Report. Payne tries to cover for Dahlia, but she insists on speaking for herself, and gives further testimony.

\subsection{The Poisoning}
\begin{tabular}{c}
I met the lawyer who was poisoned to discuss something in the cafeteria that day.\\\hline
I left my seat for just a moment, and that's when it happened!\\\hline
From what I heard, it was a liquid poison that is lethal at just 2 teaspoons.\\\hline
Not only that, I heard it was a very special kind of poison.\\\hline
So you see, I'm innocent! I wouldn't even know where to get a poison like that!\\\hline
\end{tabular}\\
\\
Mia wonders if there truly was a way for Dahlia to get her hands on such a poison, and realizes that she could have worked through her then-girlfriend, Dee, who worked in Pharmacology. \\
\\
Dahlia counters by asking how she could have carried the poison, as she and the courthouse were both searched heavily; the answer is, of course, that she gave the container to Arcadia as a gift. Further, if the crime lab were to analyze the bottle, they would likely find traces of the poison. This enrages Arcadia, and after Mia tells her that Dahlia only dated her because of the necklace, Arcadia goes into a rage and runs out of the courtroom, snagging the necklace from Mia on the way out. When captured by the bailiff and brought back to the courtroom, it is revealed that she ate the necklace. Mia's face goes pale and she panickedly asks for the trial to be stopped, as Arcadia may have ingested deadly poison. \\
\\
However, as Arcadia stands healthy, Payne takes this as crucial evidence that the bottle did not actually contain any poison. He, condescendingly, remarks that Mia gave a valiant effort, and that he too would trust this witness with his life. The Judge agrees that Dahlia no longer has any suspicion, however Arcadia then pipes up that she has more to say from her conversation with Dee:\\
\begin{tabular}{c}
Dee: That girl... You shouldn't see her anymore. \\
Arcadia: Hey! It's none of your business! \\
Dee: I'm telling you for your sake. If you continue to see her, it's going to be bad news. \\
Arcadia: Y-You're lying! \\
Dee: Just listen to me. There's something you need to know about that girl... ...\\
Last night, someone stole some poison from our lab. \\
Arcadia: P-Poison...?\\
Swallow: The same thing happened eight months ago. A drug sample was stolen. \\
She came to the lab that time, too. It could only have been her! That girl is a thief! \\
Arcadia: Stop it! D-Don't talk about her like that! \\
\end{tabular}\\
She also adds that
\begin{center}
There's one more thing... After I pushed her that day... I got worried and came back to have a look. And she was there... Dollie was right there. She was crouched down next to her... 
\end{center}
Mia makes the obvious conclusion that Dahlia stole the poison to kill someone, but then must figure out who she was planning to kill. The answer, is Arcadia. \\
\\
However, this leads directly to the question of proof. Mia recognized that Dahlia must have been planning to poison Arcadia through her cold medicine, and so the medicine is likely poisoned. Seeing an opportunity to prove its lethality immediately, she challenges Dahlia to take some medicine right now, causing her breakdown. \\
\\
Payne is left flabbergasted, having not been a part of the trial for the last part, and insists that the defense has no evidence. However, Mia recalls his statement that he ``would trust this witness with his life'', and challenges him to take some medicine, which causes him to breakdown as well. Before giving his verdict, the Judge then asks Mia how she knew Dahlia, however Mia declines to answer.

\begin{center}
{\Large Not Guilty}
\end{center}
