\section{Turnabout Sisters}

Arcadia's first trial, where Maya Fey is accused of murdering her sister, Mia Fey. Starting evidence is 
\begin{itemize}
\item Attorney's badge
\item The Thinker
\item Glass shards
\item Receipt
\item Mia's Autopsy Report
\item Maya's Cell Phone
\item Wiretap
\end{itemize}

Starting profiles are all but Redd White.

\subsection{Trial Begins}
\textit{Music: Court Begins 2001}\\
The trial begins rather plainly, with the Judge asking for Edgeworth's opening statement
\begin{center}
Thank you, Your Honor. The defendant, Ms. Maya Fey, was at the scene of the crime. The prosecution has evidence she committed this murder... and we have a witness who saw her do it. The prosecution sees no reason to doubt the facts of this case, Your Honor. 
\end{center}

He then proceeds to call his first witness: Dick Gumshoe. He asks him for the details of the murder, which add the \textbf{Floor plans} to the Court Record (Logic and Trick). He then asks for Gumshoe why he immediately arrested Ms. Maya Fey.

\subsection{Maya Fey's Arrest}
\textit{Cross Examination - Moderato 2001}\\
\begin{tabular}{p{11cm}}
As soon as the phone call came in, I rushed to the scene!\\
There were N people there already:\\
The defendant, Ms. Maya Fey, and the lawyer's friends. \\
I immediately arrested Ms. Maya Fey!\\
Why? We had a witness account describing her!\\
The witness saw Ms. Maya Fey at the very moment of the murder!\end{tabular}

At the end of the testimony, Maya throws a piece of paper at Arcadia:
\begin{center}
"When my sister couldn't find any contradictions in a witness's testimony she would bluff it and press the witness on every detail! The witness always slips up and says something wrong... It worked lots of times!"
\end{center}
The problem is that this isn't particularly *hard* evidence, which when pointed out will jog his memory.

\subsection{Hard Evidence}
\begin{tabular}{p{11cm}}
After securing the suspect, I examined the scene of the crime with my own eyes.\\
I found a memo written on a piece of paper next to the victim's body!\\
On it, the word "Maya" was written clearly in blood!\\
Lab test results showed that the blood was the victim's!\\
Also, there was blood found on the victim's finger!\\
Before she died, the victim wrote the killer's name!\\
How you like that? That's my "hard evidence"! \\
\end{tabular}

Here, the contradiction is with the autopsy report, which does not leave enough time for the victim to have written a name (Objection 2001). However, after pointing this out, Edgeworth will update the report
\begin{center}
A second autopsy was performed yesterday, at my request! "Death was almost immediate due to a blow from a blunt object... But there is a possibility the victim lived for several minutes after the blow." I received these results this morning. 
\end{center}

In any case, Edgeworth will call the second witness to the stand: April May. After some introduction (Congratulations Everybody), she testifies.

\subsection{Witness's Account}
\begin{tabular}{p{11cm}}
It was, like, 9:00 at night. I looked out the window, y'know! \\
And then, oooh! I saw a woman with long hair being attacked!\\
The one attacking her was the mousey girl sitting in the defendant's chair!\\
Then the woman, like, dodged to one side and ran away!\\
But that girl, she caught up to her and... and... She hit her!\\
Then the woman with long hair...\\
She kinda... slumped.\\
The end. That's all I saw. Every little bitsy witsy! *wink* \\
\end{tabular}

This is another bluff: that April May did not actually see Maya, since she is not mentioning the striking outfit that Maya was wearing. She will scoff that she didn't think the details were necessary, but then give more testimony.

\subsection{Witness's Account II}
\begin{tabular}{p{11cm}}
I did see everything! I did! \\
The victim--the woman--dodged the first attack and ran off to the right.\\
Then the girl in the hippie clothes ran after her...\\
And she hit her with that weapon! I saw it! I did!\\
That... that clock! Um... the kinda statue-y clock? "The Thinker," I think?\\
Well? Does the accuracy of my report not startle you? Tee hee! \end{tabular}

The contradiction is that Miss May should not have known the statue was a clock. After some back and forth, she claims that she knew it was a clock because she heard it that night. This, however, is also not possible, as the clock could not have rung, as it is missing its machinery.

Edgeworth then points out that while the clock is empty now, there is no evidence that it was empty the night of the crime. However, there is: Maya's cell phone. April then claims that she knew the statue was a clock because she saw it before, at some store. This, too, is not possible, as the statue was made by Larry, not bought in a store. The Judge then asks the witness how she knew it was a clock, however she is uncooperative (Cornered 2001). The Judge then turns to the defense, and asks if they have an opinion: they must bluff that April was wiretapping Mia, and heard then.

Either the party or the Judge will all but accuse April of murder, but she will then reveal she has an alibi: the bellboy was giving her room service at 9:00. Edgeworth then butts in that, voila, that while the witness appears to have committed another crime, her testimony stands! The Judge asks the defense if they have anything to say, and they need to call the bellboy to the stand (Suspense).

\subsection{Miss May's Room Service}
\textit{Cross Examination - Allegro}\\
\begin{tabular}{p{11cm}}
I am the head bellboy at the fine Gatewater Hotel, in business for four generations!\\
I believe I received a call after 7:00 in the evening from our guest, Miss May.\\
She asked for an ice coffee to be brought to her at 8:00, on the dot, sir.\\
I brought it to her at precisely the requested time, of course.\\
And I delivered the ice coffee to our guest Miss May, herself. \end{tabular}

The testimony is not very useful, and after some exasperated questioning, Edgeworth will chime in 
\begin{center}
Tsk tsk. Finally, you understand. This bellboy has absolutely no reason to lie! Now... If you have any decency, you will end this rather tedious cross-examination here! 
\end{center}

The Judge agrees, but then the defense asks for one more question, which reveals that two people were staying in the room. The defense is ecstatic, the other person in the room has no alibi, and so it's too early to reach a verdict. Furthermore, the prosecution tried to hide the presence of the other man! The Judge agrees, and the court adjourns.

\subsection{After the trial}
Arcadia asks for a full record of April May's testimony, although only one statement stayed on the record.


\subsection{Trial - Day 2}
\textit{Evidence: All but updated receipt}\\
Maya, Arcadia, and the defendant are in the lobby, discussing the case, when Edgeworth enters
\begin{center}
I received a call from the public prosecutor's office yesterday. He told me that whatever Mr. White says today, it will be the "absolute truth." No matter how you try to attack his testimony... If I raise an objection, I have it on good faith that the judge will listen to me.
\end{center}

In the trial, Edgeworth will call Redd White to the stand; if Arcadia objects, Edgeworth will apologize that he didn't think his testimony would be needed. He then asks some preliminary questions to Redd, and then asks for his testimony.

\subsection{Witness's Account}
\begin{tabular}{p{11cm}}
Let's see, it was about 8:00, I believe.\\
I was quietly perusifying... er, that's "reading" to you, some papers by the window.\\
Then I heard a bedlam coming from outside!\\
Surprised, I turned to look at the building across the way.\\
It was then I saw him: a spiky-haired man attacking a woman with long hair!\\
Needless to say that man was none other than you, Mr. Lawyer!\\
I called Miss May over at once. She, too, was flabbergasted of course.\\
The victim, she... she ran away, but you gave chase!\\
Finally there was a terrible impaction! Then it was all over... \\
\end{tabular}

If they ask for more details about what happened at the time of the strike (``The victim, she ran away...''), he will update his statement:
\begin{center}
The victim ran to the left, and you gave chase!
\end{center}
This introduces a contradiction with May's testimony, and also a strange inconsistency: why would she run away from the door? Redd insists he is not lying,  and so the Judge asks the defense to clarify who they believe is right. Indeed, both are right, which is only possible if Redd was inside the law offices. However, Redd interrupts with more testimony:

\subsection{She Ran to the ``Left''}
\textit{Moderato}\\
\begin{tabular}{p{11cm}}
Miss May's testimony was correct... as was mine!\\
When [defendant] assaulted the girl, she first ran to the left.\\
And [defendant] you hit her, savagely! That is what I saw.\\
Next, with the last of her strength, she ran to the right.\\
\[Defendant\] chased her, and delivered the final blow.\\
That is what Miss May saw.\\
You see? [Defendant] hit her twice!\\
Don't you remember, Mr. Lawyer? (optional)\\
\end{tabular}

This contradicts the autopsy report. Redd, stressed, revises his testimony.

\subsection{The Two Accounts}
\textit{Allegro}\\
\begin{tabular}{p{11cm}}
Umm, well, see--I looked at the other window when I heard that thing fall.\\
Then, the next moment, I saw Miss Mia run to the left!\\
The killer, [defendant], attacked her... but she dodged.\\
Umm... and then...\\
She turned, and ran for the door!\\
Then [defendant] did her in with a single blow! Thwap! \\
\end{tabular}

If they ask about what ``that thing'' was, he'll mention the glass light stand, and add a statement to his testimony:
\begin{center}
A light stand was lying on the floor when I looked.
\end{center}

However, he couldn't have seen the light stand before it fell, and after it fell it was unrecognizable. This looks fatal, however Edgeworth comes in and suggests White confess to committing the wiretapping, and it was then that he saw the light stand.

\subsection{The Wiretapping}
\begin{tabular}{p{11cm}}
It was the beginning of September... the week before the murder.\\
I had entered the Fey \& Co. Law Offices.\\
Of course, I had done so to place the wiretap.\\
That is when I saw this glass light stand. \\
\end{tabular}

Unfortunately, there's no real contradiction there, and after some questions, Edgeworth will cut him off and say it's over. When Arcadia gives up, Maya's powers will kick in, and she will channel Mia (if Arcadia is alone, she'll pass out from shock, and reconvene in the lobby:
\begin{center}
When you accepted your defeat in court... It appears that was enough of a shock to awaken Maya's true powers. \\
I don't have much time, Maya's powers are still weak. Now listen. You've already won. You have that Receipt in the court record, right? Look at the front of the receipt!\\
That's right, I bought that stand the day before I was killed!\\
\end{center}

Court will reconvene shortly afterwards, with the Judge asking if Arcadia is all right. However, once the cross-examination reconvenes, Arcadia will present the contradiction. The Judge will remark that it is about time to deliver his verdict, however Edgeworth will ask the Judge for a day's delay, as there has yet not been any concrete proof presented. The Judge will be willing, however then Mia will write a note and throw it to Mr. White. His face will fall,
\begin{center}
What, no way, this is imfoprosterious
\\
That is a list of all the businessmen, politicians, and celebrities you blackmailed. That list is burned into my memory, no matter how many records you steal, I'll always know. Now, I could release this list to the media, or maybe just recite them right now?\\

S-s-stop! Desist! Halt!...\\
.. I... I confess. I confess. I... I did it. I hit her. I hit Miss Mia with "The Thinker"! ... \\
\end{center}

The Judge will then congratulate the defense on a ``spirited'' defense.
\begin{center}
{\Large Not Guilty}
\end{center}

\subsection{After the trial}
Mia will help Arcadia with the trouble the party is having, but also ask that they try to make it back to the office tonight, say at 8pm?