
\section{Events}
\subsection{The DL-6 Incident}
\label{events:dl6}


\subsection{Kidnapping of Dahlia Hawthorne}
\label{events:kidnapdh}

\subsection{The Black Canyon Conjunto}
\label{events:bcc}
A thousand years ago, when Grima first attempted to destroy the world, the two major continents of the world were united under one rule: the Empire of Archanea. The Emperor, Primidux, brought together the finest men and women of the Empire to combat this threat:\\
\begin{tabular}{c c|c c}
Sabeline & Cohdopia & Yorya & Zheng Fa \\
Durgano & Ferox & Cacto & Ferox \\
Buckeye Ro & Ylisse & Thubberd & Cohdopia\\
Burvanen & Borginia & Wayreen & Ylisse\\
Dowell & Cohdopia & Bell & Cohdopia \\
Mosto & Ylisse & Hillinnian & Ferox\\
Ischul & Ferox & Shir  & Cohdopia \\
Melbacke & Nestra & Rosegard Lyne & Ylisse \\
Bethany & Cohdopia & Validar & Plegia \\
Glen & Ylisse & Pinnick & Cohdopia\\
Nor & Ferox & ``Happy'' Val & Ferox \\
Dunlap & Cohdopia & Jomax & Ylisse \\
\end{tabular}\\

Sorted by origin:\\
\begin{minipage}[l]{0.5\textwidth}
\begin{itemize}
\item Ylisse
\begin{itemize}
\item Buckeye Ro
\item Mosto
\item Glen
\item Wayreen
\item Rosegard Lyne
\item Jomax
\end{itemize}
\item Ferox
\begin{itemize}
\item Durgano
\item Ischul
\item Nor
\item Cacto
\item Hillinnian
\item ``Happy'' Val
\end{itemize}
\end{itemize}
\end{minipage}
\begin{minipage}[r]{0.5\textwidth}
\begin{itemize}
\item Cohdopia
\begin{itemize}
\item Primidux
\item Sabeline
\item Dowell
\item Bethany
\item Dunlap
\item Thubberd
\item Shir
\item Pinnick
\end{itemize}
\item Other
\begin{itemize}
\item Plegia - Validar
\item Borginia - Burvanen
\item Nestra - Melbacke
\item Zheng Fa - Yorya
\end{itemize}
\end{itemize}
\end{minipage}
Important lore:
\begin{itemize}
\item Mosto
Mosto was an \textit{elven cleric} of Naga and the one who managed to perform the Awakening rite and seal away Grima. In recognition, Mosto rose to great fame in the Ylissean region, and after the Schism, became the First Exalt of Ylisse. Exalt Mostyn, the predecessor of Exalt Emmeryn, is named after Mosto.

\item Melbacke
Melbacke was the finest Nestri \textit{bard}, specializing in singing and dancing.

\item Validar
Validar was a \textit{human wizard} and strong ally of the Conjunto. However, as Grima was sealed away, he managed to impart some of his life force into Validar, creating a vessel to support him when he rose again. Sly-tongued, as the Shield of Seals was disassembled, he convinced the Cabinet to entrust him with the gemstone Sable, which he hid to ensure the Awakening ritual could not be performed again.

\item Primidux
Primidux became a national hero in Cohdopia, and after his death a gold statue was created to symbolize the might of Cohdopia. In the intervening years, this statue evolved into a symbol of Cohdopia itself, alonside the butterfly H\=ato and the flower Farasha. Currently, Cohdopia is split into Babahl and Allebast, and both nations hold what they believe to be the real Primidux Statue.

\item Wayreen
Wayreen was a \textit{human monk} with excellent insight into others' motives. He sensed the change in Validar's character after the fall of Grima and recognized that he may use Sable to aid Grima in the future. To this end, Wayreen secretly established Highsleux Monastery in southern Ylisse and worked to track the locations of the Gemstones and secure the knowledge needed to defeat Grima when his reawakening occured. 
\end{itemize}
