\section{Items}
\subsection{Babahlese Ink}
\label{items:ink}
A vial of the special ink from Babahl. Burns with distinctive green flames. Provides advantage on skill checks when used to forge documents or conterfeit currency, and reduces the cost of copying spells by 10gp per level. This vial contains enough ink for 10 pages of documents, 10 levels of spells, or 50 bills.

\subsection{Cupboard of Storing}
\label{items:cupboard}
This worn brass door knob has a dimly glowing letter C on its circular face.


Holding the door knob in the air, as if holding one belonging to a real door, a shimmering door projects in the direction the knob is pointing. Turning the handle and opening the door will reveal a cupboard with 10 shelves. At any one time, 5 shelves can be seen, only being moved by use of a pulley found inside the cupboard.


Each shelf is 4 feet wide, 1.5 feet deep, and has 2 feet of free space above it. A shelf's weight capacity is 100lb's and exceeding this will cause the shelf to disappear, tossing the contents of the shelf on to the floor.


If the Brass Knob is attached to a wall, or a real door, it is inert until removed.


Placing a Brass Knob inside an extra dimensional space created by a Bag of Holding, Portable Hole, or similar item instantly destroys both items and opens a gate to the Astral Plane. The gate originates where the one item was placed inside the other. Any creature within 10 feet of the gate is sucked through it to a random location on the Astral Plane. The gate then closes. The gate is one-way only and can't be reopened.
%https://www.reddit.com/r/DMAcademy/comments/9hzbpu/a_brass_door_knob_an_alternative_to_the_bag_of/

\subsection{Emblem of Mini/Buckle of Wumbo}
\label{items:wumbo}
A magical item in the shape of a letter ``M'', made of basalt. Contains 1 charge each of \textit{reduce} and \textit{enlarge}, which are cast by holding the item so that it looks like an ``M'' for \textit{reduce}, and upside down (``W'') for \textit{enlarge}. Casting \textit{identify} on this artifact reveals only half of its properties, corresponding to the orientation of the object. Each charge has a 25\% chance of recharging each dawn.

\subsection{Falchion}
\label{items:falchion}
A greatsword that together with the \linkto{items:fireemblem} are the Ylissean royal treasures. Forged from one of  \linkto{religion:naga}'s fangs, the sword can be empowered through the \linkto{spells:awakening} ritual.

\subsection{Figurine of Wonderous Power (seagull)}
\label{items:peeko}
A statuette of a seagull, carved out of driftwood. Acts as a normal \textit{Figurine of Wonderous Power}, and when used allows the user to cast \textit{Animal Messenger} on it. The creature contained in the figurine is a \textit{fey} seagull, previously the familiar of a now-dead Sorceress that was bound to the figurine when it was passed to the widower (\linkto{people:mrbriney}). As such, the seagull, Peeko, is primarily interested in returning to Mr. Briney, however she will still follow the commands of the owner of the figurine.\\
\\
When used by Mr. Briney, the seagull may exist in physical form indefinitely.

\subsection{Honeycomb necklace}
\label{items:honeycomb}
A \textit{cursed} necklace with a small piece of honeycomb attached. When worn, gives wearer disadvantage on all checks involving items containing the letter ``B'', and if their armor contains the letter ``B'', attacks against them have advantage. 


\subsection{Lide's Earring}
\label{items:lideearring}
A \textit{magic} earring given to \linkto{people:tslil} that, through \textit{Disguise Self}, conceals his Mark of Grima on his right hand.

\subsection{Necklace of Grima}
\label{items:grimanecklace}
A \textit{magic} necklace with a pendant of the Mark of Grima. When worn, the bearer takes the form of a \textit{Tiefling} (and looks exactly like \linkto{people:validar}'s Tiefling form), as if under the effects of \textit{Alter Self}.

\subsection{Pizza Dog}
\label{items:pizzadog}
A \textit{magic} trinket with an engraving of a dog, about 4 inches long, with circular marks on it (pepperoni) and the 	engraving surrounded by a rounded border (crust). When heated to 425 degrees Fahrenheit (for example, through \textit{Heat Metal}, the trinket grows to twice its size. While enlarged, allows the casting of \textit{Silence}. The item may be heated in this way once every two days.

\subsection{Red White's Cursed Items}

\subsubsection{Boots of Mysterious Stepping}
\label{items:boots}
A \textit{cursed} item that allows the wearer to cast \textit{Misty Step} twice per short rest. When cast within 30 feet of a hostile creature, the boots instead teleport the wearer to immediately in front of the most dangerous creature in range.

\subsubsection{Greased Cleaning Rod}
\label{items:rod}
A \textit{cursed} item that, when used to clean a firearm, grants that weapon +2 on attack rolls. However, the misfire rating increases by 3. This effect lasts until a short rest is spent cleaning the affected firearm.

\subsubsection{Silk Belt}
\label{items:silkbelt}
A \textit{cursed} item that increases its wearer's movement speed by 10 feet, however if utilized the wearer must make a DC 15 DEX saving throw or trip and fall prone.

\subsubsection{Stone Bracers of Protection}
\label{items:bracers}
A \textit{cursed} item that increases its wearer's AC by 2 if they are not wearing armor, however also causes the wearer to fail any saving throws against spell effects and grants casters advantage on spell attacks targeting the wearer.

\subsubsection{Tortoiseshell Amulet}
\label{items:tortoise}
A \textit{cursed} item that, if held while casting a spell that requires a roll, grants advantage on that roll. However, until the end of their next turn, the wearer receives the following effects:
\begin{itemize}
\item Speed is halved
\item -2 to AC and Dexterity saving throws
\item Cannot use reactions
\end{itemize}
Additionally, on their next turn, the wearer can use either an action or a bonus action, not both.

\subsubsection{Tower Key}
\label{items:redkey}
A \textit{cursed} item that opens Red White's tower, however locks the door when closed. Looks like a thick electrum bracelet.

\subsubsection{Yew Shield}
\label{items:yewshield}
A \textit{cursed} item that allows Druids to use it as a spellcasting focus, however it breaks the concentration of any spell being cast.




\subsection{Sender Block}
\label{items:senderblock}
Requires attunement to make or receive calls, but not to speak. Allows the user to contact another Sender Block or Dial Stone by expending a charge, as long as the appropriate condition is met and both the caller and the target are within the same network:
\begin{itemize}
\item     Sender Block: The caller must know the target's name and face
\item     Dial Stone: The caller must know the target Stone's name
\end{itemize}
A call lasts until 10 minutes have passed without the owner of either device speaking.


The price of a sender block depends on its charge capacity and recharge rate, typically
\[ price = 3 * capacity + 2*recharge \]
The most common models are the (1,1d1) for 5gp, (5,1d4) for 20gp, (10,1d6) for 35gp, and (20,3d6) for 80 gp. 


\subsection{Shield of Seals}
\label{items:fireemblem}
A shield that together with the \linkto{items:falchion} are the Ylissean royal treasures. The shield has five insets for its Gemstones: Argent, Gules, Azure, Vert, and Sable; however, only Argent is currently present. Allows one with Exalted blood to perform the \linkto{spells:awakening} ritual, although the full complement of gemstones are required for maximum effect.

\subsection{Spade of Detection}
\label{items:detectspade}
A \textit{magic} broach made of purple jade and in the form of a Spade. When within five feet of a source of magic (other than itself or other \textit{detection} items), it lets off a faint glow.

\subsection{Thalassa's Bracelet}
\label{items:bracelet}
A magical bracelet made of a unique metal alloy that fits its bearer's wrist perfectly, and thus feels tight if the bearer is tense. Grants $+2$ to Insight and Perception checks on targets the bearer can see.\\
\\
If the bearer is a descendent of \linkto{people:thalassa}, this item alerts the bearer when someone in the field of view is actively lying or hiding something from you, and further grants advantage to Insight checks in this situation.

\subsection{Thinker Statue}
\label{items:thinker}
A stone statue of ``The Thinker''. It is secretly also a clock, which announces the time in \linkto{people:larry}'s voice as ``I think it's \{TIME\}'' when its head is turned. \\
\\
The statue works because it is enchanted with \textit{Magic Mouth}, which when activated reads the time from a clock inside the base of the statue.



\subsection{Magatama}
\label{items:magatama}
A jade, comma-shaped bead that can store spiritual power. Casting \linkto{spells:empower} fills the Magatama with charges, after which it cannot be filled again for 1d3 weeks. While empowered, the Magatama glows with a faint green color, and if touching the skin of the person it is attuned to, will vibrate and expend a charge when someone within 5 feet is actively lying or hiding something from you.