\section{Places}

\subsection{Borginia}
\label{nations:borginia}

\subsection{Cohdopia}
\label{nations:cohdopia}
Split into two nations, Allebahst and Babahl, in Naga 1002, 

\subsubsection{Allebahst}
\label{nations:allebahst}
\subsubsection{Cohdopian Normal School}
\label{places:cns}
Unlike the \linkto{places:arcaneinstitute}, the Cohdopian Normal School produces items in which magic is only a supporting element, if it exists at all. While neither school really produces weapons, an alumnus of CNS, Cole Grande, was the first to construct a gun some 75 years ago, which has been refined ever since to the variety of guns we have today. Further, while the Institute's magic is primarily of the \textit{evocation} and \textit{illusion} schools, the CNS largely specializes in \textit{transmutation} and \textit{abjuration}.
\subsubsection{Babahl}
\label{nations:babahl}
National symbol is a butterfly, called a ``H\=ato''.

\subsection{Plegia}
\label{nations:plegia}

\subsubsection{Grimstake}
\label{places:grimstake}

\subsection{Regna Ferox}
\label{nations:ferox}

\subsubsection{Ferox}
\label{places:ferox}

\subsection{Ylisse}
\label{nations:ylisse}

\subsubsection{Arcane Institute}
\label{places:arcaneinstitute}
The gem of Ivy University and central to the Losokyan way of life, the Arcane Institute develops items that allow everyone to benefit from the conveniences of magic. Some of the Institute's most famous inventions include
\begin{itemize}
\item Sender blocks and the Red network, which allow for instantaneous communication for any two people within the network\\

\item Lights\\
These come in various sizes, intensities, and colors, although their price increases the further from ``baseball-sized 20' range white''. These also require \textit{serifs} from a magic font to run. Many buildings run a connection to the main font in the Institute, but portable fonts and font generators are also available.
\item Portable fonts, which are organized into how much \textit{serifs} they contain. In increasing volume, the primary sizes are ``Q'', ``V'', ``N'', and ``F''. 
\item Cameras, onamonapoetically called ``Shashin''; these print their pictures after a short delay (think polaroid)
\item \st{Action} Video cameras, however they can typically only record in greyscale and require \textit{serifs} to run.
\end{itemize}

\subsubsection{Dusky Bridge}
\label{places:duskybridge}


\subsubsection{Eagle Mountains}
\label{places:eaglemountains}
A mountain range opposite Losokyo on Yam Lake. Home to Hazakura Temple and Dusky Bridge, however it has been mostly abandoned since the ``murder'' of Dahlia Hawthorne, with one notable exception being the murder of Valerie Hawthorne. Because of this, while the road to Dusky Bridge is still followable, the area away from the temple is still fairly wild, with a base 20\% chance of encountering hostile wildlife during a given period of time. Beyond the temple, the mountains are much more untamed, with a base 40\% chance of encounter.  In such an instance, roll a d20 to determine what appears:\\
\begin{center}
\begin{tabular}{c c c}
Roll & Outskirts & Heart \\\hline
1 & Swarm of Poisonous Snakes  & Goblin party \\
2-5 & Dire wolves & Black Bears \\
6-10 & Black Bears & Giant Insects \\
11-15 & Giant insects & Swarm of Ravens \\
16-20 & Swarm of Bats  & Swarm of Insects \end{tabular}\end{center}

\subsubsection{Kurain Village}
\label{places:kurain}

\subsubsection{Losokyo}
\label{places:losokyo}
A large city on Gourd Lake that serves as a trade connection between the interior of Ylisse and the ocean and capital, \linkto{places:ylisstol}. Contains several locations of interest:
\begin{itemize}
\item Gambling
There are two main games of chance: horse racing and the lottery. Horse racing takes place in the open fields to the west of the city, but is not particularly well known. The lottery is much more popular, and is run in a ``powerball'' style. To enter, one buys a ticket for 2 silver and chooses six numbers, between 1 and 4, 6, 8, 10, 12, and 20 inclusively and respectively. Finally, one chooses the ``Power ball'', which takes values on the ``00'' die. The rewards\footnote{Expected winnings are 1.56 s, so expected value is -0.44, which is worse than the actual Powerball's -0.26} are as follows:
\begin{tabular}{r r}
Match 6 + powerball & 2d4 * 10,000 p (1,000,000 s) \\
Match 6 & 1,000 p (100,000 s) \\
Match 5 + powerball & 50 p (5,000 s) \\
Match 5 & 10 g (100 s) \\
Match 4 + powerball & 10 g (100 s) \\
Match 4 & 7 s \\
Match 3 + powerball & 7 s\\
Match 3 & 4 s \\
Match 2 + powerball & 4 s\end{tabular}

\item Sunshine Coliseum

A large entertainment complex for stage shows. The Steel Samurai and the Jammin' Ninja have both run shows here for the last two years, although the Jammin' Ninja has declined in popularity and rarely plays; and Troupe Gramarye runs performances every other Honapon.

\item Magical trinkets

Magical Marc's Radial Shack \\
(closed) Rinea (closed after owner was found dead in the Tol river a few months back) \\

\item Clothing

Lordly Tailor


\end{itemize}


\subsubsection{Monastery of Highsleaux}
\label{places:highsleaux}
Established by the \textit{conjunto} Wayreen shortly after the fall of \linkto{religion:grima}, the Monastery safeguards the knowledge of the Awakening rite and tracks the locations of the sacred Gemstones. Some thirty years ago, a monk tracking the location of Sable encountered Lide and her son, \linkto{people:tslil}. Recognizing the danger posed by the child, the monk worked with Lide, disguised as ``Millibette'', to save her child from his fate, staging an Orc attack to buy her time to escape to Highsleaux. The monk, however, perished at Validar's hand during the fight.

\subsubsection{Olivine City}
\label{places:olivine}
A large Earth Genasi city in/under the Eagle Mountains. Its entrances are hidden and largely unknown to the greater world, however 20 years ago \linkto{people:redd} discovered one of its outposts and its guard, \linkto{people:philby}. 14 years ago, the Losokyo area was wracked by a large earthquake which caused part of one of the outer tunnels and entryways to the city to suffer serious damage and created an opening to the outside near the mouth of the Eagle River on Yam Lake. However, the damage also heavily obscured the ``trick'' for revealing the entryway into the city.

\subsubsection{Ylisstol}
\label{places:ylisstol}

\subsection{Zheng Fa}
\label{nations:zhengfa}