\section{Spells}
\subsection{Empower}
\label{spells:empower}
\begin{tabular}{c|c|c|c}
Level & Casting Time & Range/Area & Components \\\hline
1 & 1 Action & Touch & S \\
\\
Duration & School & Attack/Save & Damage/Effect \\\hline
Instantaneous & Divination & None & Buff \end{tabular}\\
Fills a \linkto{items:magatama} with 2d6 charges of spiritual energy, allowing it to function.\\
\\
When cast at a higher level, the number of charges restored increases by 1d6 for each slot level above 1st. 

\subsection{Channel Dead}
\label{spells:channel}
\begin{tabular}{c|c|c|c}
Level & Casting Time & Range/Area & Components \\\hline
2 & 5 Minutes & Touch & S, M* \\
\\
Duration & School & Attack/Save & Damage/Effect \\\hline
(C) 1 Hour & Divination & None & Shapechanging \end{tabular}\\

You kneel and move your hands in an arcane pattern, extending your consciousness into the abyss. Using the name and face of the deceased, you find their spirit and, if the spirit is willing, the spirit returns to the world of the living, using your body as a vessel. Your body and clothes adjust to match the form of the deceased before their death, although some characteristics, such as hair color, do not change. Your consciousness is suppressed during this time, as you have no connection to the physical world, except through your concentration of this spell. As such, your only possible action is to end the spell.

Channeling a spirit of level higher than the casting level of this spell requires an ability saving throw using your spellcasting ability. The DC is 10 + the spirit's level. On a failure, you are unable to end the spell early, and are unable to use this spell again for 1d4 days.

If the targeted spirit is being channeled at the time of casting, the two casters contest control by rolling a d20 and adding their spellcasting modifier. On success, the winner takes control of the spirit, while upon failure the spell ends.

This spell's maximum duration increases when you reach 5th level (8 hours), 11th level (1 day), and 17th level (1 week).

*Requires the deceased's name and knowledge of their face