\subsection{Session 11 Prep}

Facts decided in the previous session:
\begin{itemize}
\item Rinea is from Gaga, moved to Losokyo 15 years ago
\item Gaga is a city on the forested peninsula north of Losokyo
\item BlueCorp is about 30 minutes east of Ivy University
\begin{itemize}
\item BlueCorp has 25 stories, and has large blue `B's on the faces of the building
\item The building also spans the entire width of its block, with entrances on two roads
\item There are no manholes, although there are drains
\item The entrances are guarded, and have two layers of doors, the outer one is always unlocked.
\end{itemize}
\item There is a bar between BlueCorp and the main road
\end{itemize}

State of the game:
\begin{itemize}
\item In a bar near BlueCorp
\item Investigating Halcyon's suicide
\item Interested in the SL-9 incident
\item Mia has been asked to investigate the general perception of BlueCorp
\item The party has asked Lana to meet vis-a-vis the SL-9 incident
\item Klob is looking to talk to his ``criminal contacts''
\end{itemize}

What do I need to prepare for this session?
\begin{itemize}
\item How should the meeting with Lana Skye play out?
\item What should Mia find out about BlueCorp?
\item What sort of useful info could the party find out at the bar?
\item What is the bar?
\item What should a meeting with Redd look like?
\item How can Klob's contacts be useful?
\end{itemize}

Lower priorities:
\begin{itemize}
\item Norric wants to learn potionmaking
\item Who are the Five Fists bandit crew? (that killed San Juro's wife)
\end{itemize}

Background plot events:
\begin{itemize}
\item Mia needs to start investigating Redd White
\item Troupe Gramarye needs to have the Quick-Draw Shoot'em accident
\end{itemize}

\subsubsection{The Bar: Erithon Ales}
Music: Professor Layton vs. Phoenix Wright, Labyrinthia\\
The bar is about halfway between BlueCorp and the main road. It is medium sized, think Frazier's. Inside, there is a halfling, Otto Dafey, who can give some information:
\begin{itemize}
\item BlueCorp is an information-gathering company, and the CEO is a bit of an eccentric guy
\item He is happy that the SL-9 incident was resolved
\item He is a fruit vendor
\end{itemize}

\subsubsection{Mia Fey and BlueCorp}
The party asked Mia Fey to investigate what the general perception of BlueCorp is. An initial glance through her notes will tell her that BlueCorp mostly keeps a low profile in the public in terms of what it actually does. Skimming her profiles of important people, she can't find any references to BlueCorp or Redd White, however she'll ask around to see what she can learn.

She will eventually get a clue when she talks to her former boss, Marvin Grossberg, upon reading his reaction to her probing, and investigate BlueCorp much more deeply. This breakthrough needs to occur while the party is unreachable, however.

\subsubsection{Lana Skye and the SL-9 Incident}
Music: Swimming, anyone?\\
The party asked Detective Bruce to schedule a meeting with Lana Skye. The next day, the detective on duty will call them to say that Lana Skye is entirely unavailable at least until the trial concludes, but she asked that Lead Detective Damon Gant meet with them, and he will be available the following evening. 

Damon Gant will be very proud, but nice, and also slightly unwilling to discuss the exact details of the case before the trial. He will say that the trial is in three days, and that Lana's younger sister, Ema, is the key witness, and this is why Lana is unavailable, as she needs to both prepare for the trial and take care of a traumatized Ema. 

\subsubsection{Klob's contacts: Oyo}
Music: Drew Studio\\
Klob is a ``detective'' that works for a group called Dahomey, back in Ferox. Unbeknownst to him, this group is actually a branch of a larger international smuggling organization, Songhai. Before he left Ferox, he was told that if he talks to the owner of the Borscht Bowl Club in Losokyo and mentions Dahomey, he will be able to communicate with his group back in Ferox. In reality, the Bowl Club is the home base of Oyo, and while they are willing to facilitate communication with Dahomey, that is about all they are willing to do. If Klob wants anything from Oyo, he will need to earn their trust.

In particular, one of Oyo's number was murdered by Joe Darke, so the group will give Klob some information if he brings them the SL-9 case file. 

\subsubsection{Meeting with Redd White}
Music (Redd's Office): SoJ - The Basics of the Case\\
Upon entering BlueCorp, the party might notice an important looking conversation occurring in the corner of the lobby. If they decide to eavesdrop, they will hear Katerina and Garn talking:\\
\begin{tabular}{c}
``I'm telling you, everyone who can handle combat is either employed by the traders or too scared of the bandits to be of use''\\
``Did you try finding the ones that reportedly cleared the camp?''\\
``Of course I've considered it, all I've been able to learn is that they were newcomers to the city, Silque didn't tell me any more than that. Besides, isn't this your job?''\\
``I imagine we could work together, then. Well, if they're big enough to fight an entire bandit camp, they'll probably make a name for themselves some other way. Try checking the court records, see if any notable newcomers have been involved there lately.''
\end{tabular}\\
If the party tries to schedule a meeting with Redd, they will be delayed unless they reveal that they were the ones that cleared the bandits (which would optimally be done by showing the ledger). When the meeting occurs, Redd will be willing to share investigation results on Halcyon, however only if the party can do something for him. If he doesn't know they cleared the bandits, he will say that he needs some well-equipped adventurers to run a risky errand for him, and ask how he knows they are up to the task. His first plan is to send a troupe after the city's investigators and kill them before they return, although he doesn't describe it like that. However, upon hearing their exploits, he instead is ``impressed'', and asks them to ``raid'' an ancient Aurelian vault north of the city. This quest involves a delay, however, and so he asks where they are staying so he can deliver what he believes to be the key to the vault, as well as some additional magical items. The delay will be until about the end of the month.

\subsubsection{Miscellaneous updates}
\begin{itemize}
\item Halcyon's pact was with followers of Eitri, an ancient divine dragon that worked with artisans. Eitri is not inherently evil, however the sect in Losokyo that worships him utilizes some black magic that required the sacrifice of his cat.
\end{itemize}