\subsection{Session 16 Prep}
Start: Ser 3.

Facts decided in the previous session:
\begin{itemize}
\item Mia is dead!
\end{itemize}

State of the game:
\begin{itemize}
\item The party found shelter during the night, with Klob sleeping at the BBC and the others at the beat-up-the-dwarf bar
\end{itemize}

What do I need to prepare for this session?
\begin{itemize}
\item Beginning of Turnabout Sisters Investigation
\end{itemize}

Lower priorities:
\begin{itemize}
\item Norric wants to start learning how to pick locks
\item Norric wants to learn potionmaking
\item Who are the Five Fists bandit crew? (that killed San Juro's wife)
\end{itemize}



\subsubsection{The Investigation}
There are 5-7 locations important to the investigation

\begin{itemize}
\item Detention Center
\textit{Music: AA1 - Guard's Elegy}\\
Maya will talk about her sister, and herself, and mention that she came because Mia wanted her to hold onto some evidence: a clock shaped like ``The Thinker''; she will also mention that the conversation is probably on her sender block, since she forgot how to turn recording off. However, Gumshoe took her phone, so Maya gives them a memo so they don't forget to ask for it from him. While the party might ask to defend her, she will instead ask them to talk to another lawyer, one that Mia recommended.

(no more interaction available until the phone is retrieved)



\item Fey and Co Law Offices
\textit{Music: AA1 - Investigation Opening 2001}\\
The police will be investigating the crime scene, supervised by Gumshoe. If they ask about an autopsy report, he will hesitate and then give it. He will also return the sender block, but at first be a little apprehensive
\begin{center}
Sure! I mean, wait a second, pal! Tricky lawyer!
\end{center}
However, regardless of how the party responds, he'll return the phone. He might also boast that Maya's as good as guilty, since Prosecutor Edgeworth is on the case. \\
\\
Finally, as the group starts to leave, he'll tell them not to talk to the witness
\begin{center}
I don't suppose you're planning on talking to that witness. Anyway, you'd better not! No influencing the witness with your lawyerly ways, pal!\\
Yeah, Miss April May. I'm sorry `bout this... But I can't tell you anything about her!\\
She's not to go outside her room until the trial!
\end{center}

(he leaves after the party visits the hotel)

\item Grossberg Law Offices
\textit{Music: AA1 - Age, Regret, Retribution}\\
(out of the office until after talk to Maya the second time)\\
In the office is a very impressive painting, and if asked about it Grossberg will emphasize his desire to never part with it.

\item Gatewater Hotel
(not available until after Fey and Co)\\
\\
\textit{Music: AA DD - Suspicious People or AA1 - Congratulations, Everybody}\\	
Talking to the front desk reveals which room is May's, if they can't figure it out themselves. She will be kinda flirty, and quickly  duck away to ``freshen up so I can look the part of the beautiful eyewitness!''. The room is not a suite, however there is a small balcony. Inside, there is a table with two chairs pulled up to it, with a bottle of wine and two glasses on it. In the clothes drawer, one drawer is slightly ajar, and inside there is a screwdriver and a strange device. However, if they aren't quick about it, she'll come back and chastise them. She will be very uncooperative.

(no interaction until after talking to Maya after Grossberg)

\item Ivy University
\textit{Music: Investigation Opening 2001}
(not really available until after talking to Grossberg)\\
If the party asks Arcadia to defend Maya, she'll do it.

\item Bluecorp
\textit{Music: SM - Aether Paradise}
Redd White is unavailable, Garn and Katerina will not be very helpful.

\end{itemize}



