\subsection{Session 17 Prep}
Start: Ser 4, 1:00pm.

Facts decided in the previous session:
\begin{itemize}
\item Investigation progress
\item There is a member of BlueCorp, Shawn, who has been tracking shipping logs of the last six months, cross-referencing them with ships in the marina. He's been doing this for the past week, having made it almost through the ``S''s. His supervisor is Vaurice (he pronounces it ``Varus'', but it is actually like ``Maurice''). Klob instigated an altercation with him, and after calling the police he realizes that this could be good blackmail to hold over Klob's head in the future.\\
Additionally, Shawn works with Fekete.
\end{itemize}

State of the game:
\begin{itemize}
\item The party has just talked to April May
\end{itemize}

What do I need to prepare for this session?
\begin{itemize}
\item Beginning of Turnabout Sisters Investigation
\end{itemize}

Lower priorities:
\begin{itemize}
\item Norric wants to start learning how to pick locks
\item Norric wants to learn potionmaking
\item Who are the Five Fists bandit crew? (that killed San Juro's wife)
\end{itemize}



\subsubsection{The Investigation}
There are 5-7 locations important to the investigation

\begin{itemize}
\item Detention Center
\textit{Music: AA1 - Guard's Elegy}\\

(no more interaction available until the phone is retrieved)

After retrieving the phone, Maya will ask to listen to her sister's voice, which replays the message (she sobs as she hears her sister's voice again)\\
\newpage
\begin{tabular}{p{11cm}}
Mia! What's up? You haven't called in a while. \\\hline
Sorry, I've been so busy. How you been?\\\hline
Well, LONELY. And it's all YOUR fault. Nah, I'm just teasing. I've been great! I'm finally getting used to having my own place.\\\hline
That's good to hear. Actually, I'm calling because I have a favor to ask.\\\hline
I know, I know. You want me to hold evidence for you?\\\hline
Sharp as always! I think I'm one step closer to figuring out who ruined Mom. But I don't feel safe keeping the evidence here.\\\hline
I gotcha. So, what is it this time?\\\hline
It's... a clock.\\\hline
A clock?\\\hline
Yeah, it's made to look like that statue, "The Thinker." And it tells you the time! I thought you might like it. You always liked toys.\\\hline
Hey! I'm not a little girl anymore, Sis!\\\hline
Now, now. You know I'm only teasing. Ah, I should probably tell you, the clock isn't talking right now.\\\hline
Huh? It's not working? That's lame!\\\hline
I had to take the clockwork out. Sorry. I put some papers inside it instead.\\\hline

Papers? Is that the evidence, then? \\\hline

Hmm, well... there's a possibility that it might turn out that way, yes. Can you come by the office tonight, say 8:00, to pick it up? I'll be out and about until then.\\\hline

Okay, Sis, but I expect dinner! Something good! Like... burgers! I could really go for a good burger.\\\hline

Okay, okay. We'll hit the usual joint.\\\hline

Alright! It's a deal! Okay, Sis, see you soon!\\\hline

Yep. I'll be waiting, Maya.\\\hline

*beep* [Conversation recorded. Ser 3, 9:27 AM] 
\end{tabular}
\newpage
She will also talk about her family, how they have been mediums for generations. But also, about 15 years ago, their familiy was involved in an incident, where one man ruined her mother's life. She describes the DL-6 incident, and mentions that a man found out about it and leaked it to the press. Mia became a lawyer to investigate who it was, and it sounded like she had just made a breakthrough...

(no more interaction until after talking to Grossberg)

\textit{Music: Reminescense - Heartbroken Maya}\\
Maya will look hopeful, asking if the party was able to find the lawyer. Faced with the bad news, she resigns herself to wait for the city-appointed attorney. However, if the party decides to defend her, or convinces Arcadia to defend, she will perk up (and music changes to investigation core 2001)  (although if they offer to defend her, she'll recall a call she had with her sister about a week ago: \\
\begin{tabular}{p{11cm}}
"Today was my troupe's first time in court."\\
Wow! Really? How'd that go?\\
"It was quite the scene! Honestly, I was on edge the whole time. It's been a while..."\\
Hah! So, they crashed and burned?\\
"...They're geniuses. Some of those 'strike fear into the hearts of evil' types... The only thing they're lacking is... experience."\\
Huh, sounds like it was fun! Well, I know who to go to if I ever get into trouble now!\\
"I don't know, Maya. I think you might want to wait... give him three more years. That is, unless you want to be found guilty. They still need their training wheels." \\
\end{tabular}



\item Fey and Co Law Offices
\textit{Music: AA1 - Investigation Opening 2001}\\


(he leaves after the party visits the hotel)

\item Grossberg Law Offices
\textit{Music: AA1 - Age, Regret, Retribution}\\
(out of the office until after talk to Maya the second time)\\
In the office is a very impressive painting, and if asked about it Grossberg will emphasize his desire to never part with it.

Talking with Grossberg will at first be promising, however upon asking him to defend Maya, he will appear nervous and abruptly refuse. In fact, he tells them that ``no lawyer worth their salt will take on this case''.


\item Gatewater Hotel
(not available until after Fey and Co)\\
\\
\textit{Music: AA DD - Suspicious People or AA1 - Congratulations, Everybody}\\	

(no interaction until after talking to Maya after Grossberg)
Upon returning again, they will run into a Bellboy outside her room. He will inform the party that Ms. May is using the facilities, turn to leave, and then also say ask the party to tell her that she has a message from Mr. White, of Bluecorp. Inside, investigating will find a screwdriver and a strange device that looks like it can fit into the machinery of a dial stone. Bringing this to anyone who would know would recognize it as a wiretap. Shortly after this investigation, May will call out ``Oh bellboy? Still there?'', hopefully spooking the party into fleeing.\\
\item Ivy University
\textit{Music: Investigation Opening 2001}
(not really available until after talking to Grossberg)\\
If the party asks Arcadia to defend Maya, she'll do it.

\item Bluecorp
\textit{Music: SM - Aether Paradise}
Redd White is unavailable, Garn and Katerina will not be very helpful.

\end{itemize}



