\subsection{Session 18 Prep}
Start: Ser 5, 6:00pm?

Facts decided in the previous sessions:
\begin{itemize}
\item There is a member of BlueCorp, Shawn, who has been tracking shipping logs of the last six months, cross-referencing them with ships in the marina. He's been doing this for the past week, having made it almost through the ``S''s. His supervisor is Vaurice (he pronounces it ``Varus'', but it is actually like ``Maurice''). Klob instigated an altercation with him, and after calling the police he realizes that this could be good blackmail to hold over Klob's head in the future.\\
Additionally, Shawn works with Fekete.
\end{itemize}

State of the game:
\begin{itemize}
\item The party is about to talk to Redd White
\end{itemize}

What do I need to prepare for this session?
\begin{itemize}
\item Turnabout Sisters Investigation, day 2\\
They've done mostly everything they need to for the second day of trials. 
\item Klob and Vaurice meeting
\item Turnabout Sisters Trial, day 2
\item How does this chapter end?\\
There are two big threads to tie up:
\begin{itemize}
 \item Dissolution of BlueCorp
 \item Discovery of why Halcyon committed suicide
\end{itemize}
\end{itemize}

Lower priorities:
\begin{itemize}
\item Norric wants to start learning how to pick locks
\item Norric wants to learn potionmaking
\item Who are the Five Fists bandit crew? (that killed San Juro's wife)
\end{itemize}



\subsubsection{The Investigation}
They've mostly learned what they need to, however they maybe haven't quite realized that Mr. Grossberg is being blackmailed.

\begin{itemize}
\item Grossberg Law Offices
After having talked with Redd, the party has enough ammo to prod Mr. Grossberg into talking with them. He will reveal that Redd has been blackmailing him, but not just him, but people across positions of power. If asked, he will explain the DL-6 incident, and, if asked what he is being blackmailed for, reveal that he was the one who leaked the information.

\item BlueCorp office
(Redd will initially be busy, however if they insist on meeting with him they will be able to)\\
Redd will ask about their trip, and ask what was so important. He will deflect blame onto Miss May, saying that he didn't know about the wiretap. Finally, if they ask about the painting, he'll cool off, and ask them what they think their position is here. Then, standing up (and attaching a Broach of Shielding), he walks over to a member of the party, and punches them.
\begin{center}
Well, Mr. \emph{class}. What will you do, eh? Charge me with assault? Charge away, I welcome it! For it is YOU who will be found guilty!
\end{center}
Continue with the script, taunting them to talk to Grossberg.\\
\\
If they come back and accuse him of blackmail, Mr. White will call his secretary, and ask for the troupe to be escorted out. Any further pressure and he will change his mind, and instead call the public prosecutor's office, asking them to arrest Aleneth (or Poncho).

After the meeting, Vaurice will ask to speak with Klob, alone, and asked to identify some small rocky spheres that were found amongst a crate of stolen goods. Try to trick him into heading down to investigate the crates, and if trick doesn't work, blackmail. Once down there, disarm and lock him up.\\

\end{itemize}

\subsubsection{After the arrest}
Klob will be pulled aside by Vaurice and taken to Sthera's lair, where he will be used to threaten Norric into compliance.\\
Aleneth/San Juro will be allowed to stay with one of their contacts: Virion, rather than head to the detention center. In any case, if Norric decides to wander off by himself, he will find a copper cricket; then, when alone, he will be attacked: attempted blind with Mystherbe poison (DC 18 Constitution) and tied up (including anti-magic manacles), and taken under the city to the Eitri Shrine. 



