\subsection{Session 12 Prep}

Facts decided in the previous session:
\begin{itemize}
\item Redd has two missions for the party: retrieve the Spectacles of Spectation from Yosmight, and raid an ancient Aurelian vault
\item Redd has never been to the Aurelian vault
\item Detective Gumshoe conducted the investigation into Halcyon's suicide
\item Blaise Debeste is the current chief prosecutor
\end{itemize}

State of the game:
\begin{itemize}
\item Broderick is brawling in a bar with some dwarves
\item Klob and San are at the Borscht Bowl Club
\item Norric and Aleneth are walking in Yam Lake Park
\item About to take a time skip to the end of the month
\end{itemize}

What do I need to prepare for this session?
\begin{itemize}
\item What has Mia found out?
\item Broderick sparring school
\item How does Redd give the party the items?
\item The meeting with Gully Briney
\item The battle at White's tower
\end{itemize}

Lower priorities:
\begin{itemize}
\item Norric wants to start learning how to pick locks
\item Norric wants to learn potionmaking
\item Who are the Five Fists bandit crew? (that killed San Juro's wife)
\end{itemize}

Background plot events:
\begin{itemize}
\item Mia needs to start investigating Redd White
\item Troupe Gramarye needs to have the Quick-Draw Shoot'em accident (later)
\end{itemize}

\subsubsection{White's Tower}
Music: Professor Layton vs. Phoenix Wright, Labyrinthia\\
The bar is about halfway between BlueCorp and the main road. It is medium sized, think Frazier's. Inside, there is a halfling, Otto Dafey, who can give some information:
\begin{itemize}
\item BlueCorp is an information-gathering company, and the CEO is a bit of an eccentric guy
\item He is happy that the SL-9 incident was resolved
\item He is a fruit vendor
\end{itemize}

\subsubsection{Mia Fey and BlueCorp}
The party asked Mia Fey to investigate what the general perception of BlueCorp is. An initial glance through her notes will tell her that BlueCorp mostly keeps a low profile in the public in terms of what it actually does. Skimming her profiles of important people, she can't find any references to BlueCorp or Redd White, however she'll ask around to see what she can learn.

She will eventually get a clue when she talks to her former boss, Marvin Grossberg, upon reading his reaction to her probing, and investigate BlueCorp much more deeply. This breakthrough needs to occur while the party is unreachable, however.

\subsubsection{Klob's contacts: Oyo}
Music: Drew Studio\\
Klob is a ``detective'' that works for a group called Dahomey, back in Ferox. Unbeknownst to him, this group is actually a branch of a larger international smuggling organization, Songhai. Before he left Ferox, he was told that if he talks to the owner of the Borscht Bowl Club in Losokyo and mentions Dahomey, he will be able to communicate with his group back in Ferox. In reality, the Bowl Club is the home base of Oyo, and while they are willing to facilitate communication with Dahomey, that is about all they are willing to do. If Klob wants anything from Oyo, he will need to earn their trust.

In particular, one of Oyo's number was murdered by Joe Darke, so the group will give Klob some information if he brings them the SL-9 case file. 

\subsubsection{Meeting with Redd White}
Music (BlueCorp): SM - Aether Paradise Music \\
Music (Redd's Office): SM - Aether President Lusamine's Theme, Version 1 \\
\\
Get the items, answer any remaining questions.\\
Gordian Rope: Speak the word (Gordias) and the rope will tie itself into a secure knot. The knot cannot be untied, however.\\
Bolts of Cutting: Add +5 to STR checks for breaking physical locks.\\
Beach Trowel: +2 to WIS and DEX checks involving gardening.\\

\subsubsection{Travel north}
Music: Fire Emblem Awakening - Conquest\\
They should follow the lake, north, and near nightfall approach a small house on the lake, with the tower barely visible in the distance.

\subsubsection{Mr. Briney}
Music: Id (Serenity) \\
\\
Trade Peeko for the bag of holding and some information, get a good night's sleep.

\subsubsection{The Tower}
Music: Aether Branch Chief Faba\\
A tall, 100 foot tall, 60 foot wide, cylindrical tower, with a 20'x100' circular wall around it. One section of the wall looks like a door, however it is sealed shut with only an indentation that looks sort of like an upside down Bundt pan. The tower is protected from overcoming the wall with a material-plane-only Wall of Force over the courtyard. Inside, however, there are four large suits of armor at cardinal directions, and eight pyramidal objects on the ground in the courtyard. Getting within 20' of one of the pyramidal objects starts the encounter.\\
\\
The combat:\\
Music: Aether President Lusamine Battle Music \\
\\
Enemy: 1 Helmed Horror, 3 illusory Helmed Horrors, eight Missile Defense (tridromo)\\
\\
The Helmed Horror facing the door is the real one, the others are illusions (DC 15 Investigation). At initiative count 20, the Missile Defense system will activate, with each turret that has an enemy within 20' casting a level 1 magic missile, spreading their shots as much as possible. For each turret that activates, the wearer of the Stone Bracers will take 1 damage. If the Stone Bracers are broken, the system deactivates, however the Horror continues to attack.\\ 

\subsubsection{Miscellaneous updates}
\begin{itemize}
\item Halcyon's pact was with followers of Eitri, an ancient divine dragon that worked with artisans. Eitri is not inherently evil, however the sect in Losokyo that worships him utilizes some black magic that required the sacrifice of his cat.
\end{itemize}