\subsection{Session 12 Prep}

Facts decided in the previous session:
\begin{itemize}
\item The items are cursed
\end{itemize}

State of the game:
\begin{itemize}
\item The party just defeated the Tower guardians
\end{itemize}

What do I need to prepare for this session?
\begin{itemize}
\item What is in the tower?
\item How do they reach the vault?
\item What is in the vault?
\item What is the vault layout?
\end{itemize}

Lower priorities:
\begin{itemize}
\item Norric wants to start learning how to pick locks
\item Norric wants to learn potionmaking
\item Who are the Five Fists bandit crew? (that killed San Juro's wife)
\end{itemize}



\subsubsection{The Tower}
Music: Aether Branch Chief Faba\\
With the defenders gone, it remains to see how to get either into the tower or out of the gate. The Horror's sword acts as a key to the inner tower, which reveals a large room.

\subsubsection{The Tower: Ground level}

The ground level of the tower is largely a staging area for storing goods; there are a couple wagons inside, as well as some useful items: shortswords, hand crossbows, javelina, shovels, wheelbarrows, etc. In the center is a nice spiral staircase going up, and at 3 o'clock there is a large statue of a sea creature, a chimera of a dolphin and a pig, suckling its young. Inspecting the area around the statue reveals that it can be moved to the side, revealling a grate (DC 10 to pick, DC 15 to break) that leads to the foyer of the Aurelian vault.

\subsubsection{The Tower: Level 2}

The second level is largely a sleeping area for the bandits, should they need to spend the night here. There is assorted money left behind, totalling 7 gp, 20 ep, 18 sp, 2 cp, a set of thieve's tools, and 3 sets of stale rations. The stairwell up is blocked, however, with a sign ``Do not enter. Master only.'' and the Paradox symbol.

\subsubsection{The Tower: Level 3}
This is the Stone Golem and lair.


\subsubsection{The Tower: Higher levels}
Fourth level is the treasure room, fifth level is Redd's office.

\subsubsection{The Aurelian Vault}

The Aurelian Vault is arranged in a square with six important rooms: one in each corner, one in the center (Entrance), and one beyond the center (Treasure Room). The Entrance is rather spacious, with exits in all cardinal directions, however the northern exit is blocked by a magical forcefield, which appears to be powered by a gem on the other side. The gem is floating in a pool of liquid that is fed from a channel that diverges into two 