\subsection{Session 18 Prep}
Start: Ser 5, 12:00pm.

Facts decided in the previous sessions:
\begin{itemize}
\item There is a member of BlueCorp, Shawn, who has been tracking shipping logs of the last six months, cross-referencing them with ships in the marina. He's been doing this for the past week, having made it almost through the ``S''s. His supervisor is Vaurice (he pronounces it ``Varus'', but it is actually like ``Maurice''). Klob instigated an altercation with him, and after calling the police he realizes that this could be good blackmail to hold over Klob's head in the future.\\
Additionally, Shawn works with Fekete.
\end{itemize}

State of the game:
\begin{itemize}
\item The party is about to cross-examine the bellboy
\end{itemize}

What do I need to prepare for this session?
\begin{itemize}
\item Turnabout Sisters Investigation, day 2
\item Klob and Vaurice meeting
\item Turnabout Sisters Trial, day 2
\item How does this chapter end?\\
There are two big threads to tie up:
\begin{itemize}
 \item Dissolution of BlueCorp
 \item Discovery of why Halcyon committed suicide
\end{itemize}
\end{itemize}

Lower priorities:
\begin{itemize}
\item Norric wants to start learning how to pick locks
\item Norric wants to learn potionmaking
\item Who are the Five Fists bandit crew? (that killed San Juro's wife)
\end{itemize}



\subsubsection{The Investigation}
There are 5-7 locations important to the investigation

\begin{itemize}
\item Detention Center
April refused to go into her cell, so the guards have compromised and let her stay in the visitor's room until someone else needs it. If the party talks to her, she hates them.
\begin{center}
Hey, guess what. Actually, I, um, really hate your guts. So get lost. Because, well, I'm not cooperating.
\end{center}
However, if they ask about (or show a picture of) Redd, her facade will break for a second, but then she will demand proof that that was him.\\
(after returning with the affadavit)\\
Showing her the affadavit causes her to talk, however if the party goes soft on her she'll regain her composure and taunt them. Otherwise, she'll talk, although she doesn't have too much new information.


\item Fey \& Co. Law Offices
The following needs to happen, but the primer isn't until after meeting with Grossberg. \\
The bookshelf has files on all the cases Mia ever investigated, in alphabetial order. Here are some notable excerpts:
\begin{itemize}
\item[F:] Fey, Misty:
\begin{center}
```I have tarnished the Fey name.' \\
Leaving only these words, my mother vanished. I was determined to find the ones who had made my mother blame herself in this way. Using the E.S.P. that runs in my family, I held an audience with the dead. Finally, hints to the identities of two men surfaced. One turned out to be Marvin Grossberg, a lawyer who sold my mother's information for riches. The other was the man who sold that information to the press. This parasite, who makes his fortune on threats and coercion... this runs much deeper than DL-6."\end{center}

\item[S:] Suicides:
A collection of suicide reports, of politicians, policemen, and others, including Halcyon. There's writing on most of them: ``White''. It might be a good idea to keep some of this, in case it gets ransacked again.

\item[W:] White:
Actually, the entire ``W'' section is missing!
\end{itemize}
\item Grossberg Law Offices
Grossberg is again not in, however the room has changed in subtle and not-so-subtle ways. First, there are two pictures on the desk: ``DL-6 Incident - Exhibit A/B'', A being a picture of Misty Fey and B being a picture of Redd White. Second, the obtuse painting on the wall is gone.\\
\\
(he returns after talking to Miss May)\\
Grossberg compliments the party on their work in the trial. If asked about the photographs, he'll sort of grumble, and possibly talk about BlueCorp and Redd White, however he will retreat into thoughts afterwards.\\
(he refuses to talk until after the party has talked to Redd)\\
After having talked with Redd, the party has enough ammo to prod Mr. Grossberg into talking with them. He will reveal that Redd has been blackmailing him, but not just him, but people across positions of power. If asked, he will explain the DL-6 incident, and, if asked what he is being blackmailed for, reveal that he was the one who leaked the information.


\end{itemize}