\subsection{Session 15 Prep}
Start: Ser 2.

Facts decided in the previous session:
\begin{itemize}
\item The items are cursed
\end{itemize}

State of the game:
\begin{itemize}
\item The party just finished exploring the Aurelian vault, but still believe they are trapped inside the tower
\end{itemize}

What do I need to prepare for this session?
\begin{itemize}
\item How do they escape the stronghold?
\item When about a mile from the city, receive a call from Mia
\item What occurs on the way back?
\item Beginning of Turnabout Sisters
\end{itemize}

Lower priorities:
\begin{itemize}
\item Norric wants to start learning how to pick locks
\item Norric wants to learn potionmaking
\item Who are the Five Fists bandit crew? (that killed San Juro's wife)
\end{itemize}


\subsubsection{The Tower}
\textit{Music: Pokemon BW - Chargestone Cave (1st and 2nd levels are basic, 3rd is Deeper, 4th and 5th are Deepest)}\\

To escape the tower, all they need to do is press the dongle in the center of the ground floor. The tower has been visited twice in the last two months. Redd visited it about a week ago, and the bandits dropped off some goods about a month and a half ago. 

\subsubsection{The Trek Back}
\textit{Music: Fire Emblem Awakening - Conquest}\\
\textit{Music (Mr. Briney): Village Bridge (Harpsichord)}\\
\textit{Music (sailing): Pokemon DPP - Surf}\\
The trek back should be more or less the same as the trek there. A DC 15 investigation/nature check for herbs may find a cluster of Mystherbe, which are plant creatures that are very useful for herbalism. However, they startle easily, so picking them up incorrectly (DC 20 Nature) causes them to release a cloud of poison gas: DC 15 CON or become poisoned and blinded for 1 hour.

\subsubsection{Turnabout Sisters}
When the party is near-ish to Losokyo, they should get a call from Mia saying that she made some progress in her investigation, and also that her sister is coming tonight and they should all get dinner.
\begin{center}
Hey Klob, where were you? I tried calling earlier/yesterday but the dial stone wasn't able to connect for some reason. In any case, I've made a lot of progress on the investigation of Bluecorp that I'd like to share with you. My sister is coming by tonight as well, perhaps we could all get dinner together? How about you stop by my office around 9pm?
\end{center}

They should hopefully arrive at Fey and Co Law Offices around 9pm. When they arrive, the foyer should be dark, with the door to her office slightly ajar. Broderick should smell a faint hint of blood. Going into the main office, they should see a messy sight:\\
\textit{Music: Ace Attorney SOJ - Suspense}
\begin{itemize}
\item Numerous items on the table in disarray, although the dial stone is still standing
\item The plant knocked over, a glass light stand that had fallen over and is now largely in unrecognizable pieces
\item Mia, dead, leaning against the wall
\item A girl in really strange clothes, on the ground near Mia, sobbing, who passes out shortly after the party arrives
\end{itemize}
Further investigation reveals
\begin{itemize}
\item The Thinker, lying on the ground next to her, blood on its base
\item A receipt with ``Maya'' written in blood on the back
\item The Gatewater hotel is visible through the window, you can just barely make out the bottom of your balcony. There is a woman standing on the balcony below that one, sender block in hand and looking straight at you
\end{itemize}
Returning to the main room, Maya will come to and look dazed. There won't be much time for conversation, as Detective Gumshoe will arrive soon, find the receipt, and arrest Maya.




