\section{Redd White}
After returning from the Eagle Mountains, the party will have some downtime to learn more about the world and Losokyo. Mia will congratulate them on their success, and suggest they do some investigating in Losokyo to learn more about the goings-on in the city. Some example locations of investigation:
\begin{itemize}
\item Study: Ivy University
A small-sized campus, about the size of Johns Hopkins University, with a similar layout and red-brick motif. The main clock tower bears an engraving of a snake (asp) curls around an apple, in reference to the following legend
\begin{quote}
Once upon a time, two lads--Ademichael and Gallansteve\footnote{An alternate version of the story involves a man, Ademichael, and a woman, Gallaneve. Some people are very adamant that it is ``Ademichael and Gallen\textit{eve}, not Ademichael and Gallan\textit{steve}''}-- were lost in a thick forest and unable to find their way home. A heavy rain came, and the two quickly built a makeshift shelter to wait out the storm. Shortly after the rain ceased, Gallansteve left the shelter and came to a clearing, where an asp sat curled around an apple. The asp told Gallansteve, ``I can guide you out of this forest, however you and your partner must first demonstrate your bond''. With a flicker of its tongue, the asp turned Gallansteve into a tree at the edge of the clearing, of form indistinguishable from the other trees of the forest. ``If your friend can determine which tree you became, then I shall guide you out. Otherwise, he too shall become a tree and the two of you shall stay here forever.'' Not much later, Ademichael arrived at the clearing, where the asp explained the scenario to him. Ademichael, being a rather quick fellow (although apparently not quick enough to avoid getting lost in a forest), thinks for a second, and after walking around the clearing and taking a quick look at all the trees, correctly identifies Gallansteve\footnote{The Gallansteve tree is the only tree with dry leaves}. Impressed, the asp restores Gallansteve and fulfills his promise, and the two return home safe and sound.
\end{quote}
Ivy University is known for its \linkto{places:arcaneinstitute}, which invents items that make the conveniences of magic accessible to normal people (well, normal people with gold), and for its fierce rivalry with the \linkto{places:cns}. Students of Ivy University, called ``aspies'', compete with students of the Cohdopian Normal School, called ``normies''\footnote{I am so proud of this}, every year at the World Faire for the most impressive invention. The Sender Blocks arose out of the Faire about 10 years ago, beating out the CNS ``Dial Stone'', which relied on a mixture of machinery and magic, however was too heavy to be portable. They were cheaper and more reliable, however, so it is not uncommon to see dial stones in businesses, where there is a need to conduct a large volume of calls from one location.

Here the party might meet \linkto{people:phoenix}, a rather enthusiastic student in \linkto{places:arcaneinstitute}, who can inform the party of the above background.  who can let them into the library and talk to them about Ivy University. In this area, they can learn a large amount about the history of Ylisse and Losokyo. If the party mentions Mia to Arcadia, he will warm up immensely and gift the party a (3,1d1) \linkto{items:senderblock}, mentioning that Mia helped him out of a very sticky situation a couple years ago (Turnabout Doug Swallow). Alternatively, they can check out the \linkto{places:arcaneinstitute}.
\item Recreation: Sunshine Coliseum
They arrive just in time for a performance by the reknowned Troupe Gramarye, although the posters have been edited to reflect that Mr. Reus will not be part of the show. If any of the arcanists are present, Thalassa will pull them aside and ask them to be a volunteer for the opening act, although they will need to be bare of any magic items. During the show, Magnifi will remark that his is the ``true'' magic, of a deeper form than that of typical arcanists. To demonstrate this, he indicates towards four large blue jade symbols on the corners of the stage: a Club, a Spade, a Heart, and a Diamond. 
\begin{center}
``These artifacts can detect any magic used on this stage, from any spells cast, to those with lingering effects, and even any magical items, except for the artifacts themselves, of course. To demonstrate this, I ask for an arcane volunteer from the crowd... yes, you! Please come up to the stage.''
\end{center}
Magnifi will ask the party member to attempt to perform magic that eludes detection, but all will of course cause the artifacts to light up. Finally, Magnifi will remark that the member looks like they've seen some battle, and so ask them to give him their best shot. On a spell attack, Magnifi's cloak will billow up, obscuring his form, and then disintegrate, leaving no trace of him behind. After a beat, the spotlight will shine on the party member's seat in the audience, where Magnifi will stand up, clapping and congratulating the arcanist for a great show. As a present for cooperating, he will award the arcanist with a smaller version of a jade artifact, a \linkto{items:detectspade}, similar to the broach on Magnifi's cloak. The show then continues on, with acts of the Quick Draw Shoot'em, or making entire ships disapear.

\item Shopping: Magical Marc's and the Radial Shack

Marc and his assistant Kane have a shop where they sell traditional magic items and identify magic goods shown to them. Nearby is a circular store, the Radial Shack, which sells the campaign-unique magical items developed at Ivy University, such as Sender Blocks, Cameras (still and video), and Illuscreens (televisions). Kane might mention how he would really like to run an information security company, but unfortunately there's no room for that sort of business with Bluecorp around.

\item Legal System: Mia Fey and the Reading Room

The party can also talk to Mia about how trials run. She will explain, in sort of a fourth-wall manner, the rules of the court. She will also lend the party her copy of Evidence Law, and remark that the courthouse has a reading room that may have some books of interest.

\item Legal System: Lana Skye and the Police Station

While the party was gone, Lana, Damon, and the rest of the crew interrogated Joe Darke and found conclusive evidence that he committed the murders, particularly the murder of Niel Marshall. For his leading role, Damon Gant will be promoted to Chief of Police following the conclusion of the trial, which should happen by the beginning of the next month. Lana is, however, somewhat glum or cold, despite the good news. In any case, she can discuss some of the high profile cases in the past, such as the DL-6, IS-7, KG-8, or any of the Dahlia Hawthorne cases. 
\end{itemize}

 As word spreads of their conquest of the bandits, Fekete Artois\footnote{if friendly, he will insist on being called Karcha} will approach a member of the group and ask them to come to Bluecorp, as their president is very interested in the feats the group has accomplished.\\
\begin{center}
``Wow, are you the group that cleaned out that nasty bandit camp? That's amazing! I'm sure my boss would love to meet you.''
\end{center}
He arranges to bring the party to Bluecorp, at which point they take a lift to the 13th floor and, after a short wait, are invited into \linkto{person:reddwhite}'s conference room. White explains Bluecorp's purpose: in some sense a detective agency, although more accurately an information-gathering company, they support many efforts in Losokyo, such as lobbying and private investigation. He mentions that the party has probably already run into one of his employees, seemingly implying Lotta Hart, even though she is not actually affiliated at all. Some examples of what Bluecorp has done:
\begin{itemize}
\item Outed a smuggling ring that was bypassing the usual trade routes (this was done to eliminate a rival smuggler)
\item Revealed the use of unconventional investigative methods by the police (\linkto{events:dl6})
\item Publicized shady business practices in one of the large shopping congomerates (the CEO was having an affair with a higher-up in a rival company; this was his leverage over their CEO; when he refused to cooperate in providing deals to Bluecorp this information was publicized and the target later took his own life)
\end{itemize}
White then asks the group if they would be willing to help him with a unique information gathering task. There is an abandoned fort not too far away that White believes holds scouting manuscripts from two centuries ago, as well as likely a decent amount of abandoned artifacts and gold from when this acted as a trading post, before all trade started being routed through Losokyo. He would use his own detectives, but all of them have refused the mission, citing the bandit threat in the outskirts. Also, the fort is likely booby-trapped, but that is why he suspects the loot is still inside. However, he assumes this shouldn't be a problem for the party. He is willing to provide ``compensitorial funding'', of 200G upon a successful return and the assurance that they will sell him 75\% of the valuable items that were recovered. He is also willing to front some portion of the agreed-upon flat amount. If pressed for a magical item, he will rummage through his collection and provide \linkto{items:boots}. Once an agreement is made, White will provide the party with a``compass'', which always points in the direction of the tower\footnote{but also allows White to track the party} and an amulet that should open the gates\footnote{it will also seal them once inside}. \\
\\
The conference room is filled with knick-knacks of various types, many of which are actually either magic items or warded ones. If a party member messes with an item, roll a d10 for the effect
\begin{tabular}{c c|c c}
1 & Burning hands & 2 & Color spray \\
3 & Fog cloud & 4 & Grease \\
5 & Magic Missile & 6 & Ray of Sickness \\
7 & Silent Image (suit of armor) & 8 & Sleep \\
9 & Thunderwave & 10 & Light \end{tabular}
Upon reaching for the item, White will yell out and try to stop. After the situation resolves, White explains that he collects magical artifacts for display in this room, but many of them are dangerous and shouldn't be touched without preparation. He mentions a magical merchant in town, Marc, who he has bought many of these items from. (In reality, he is blackmailing the merchant to give him these items for free).\\
\\
Things that should occur before the party leaves:
\begin{itemize}
\item Mia should have a way of contacting the party, as she will do so upon their return as Turnabout Sisters begins
\end{itemize}
\subsection{Sidequest: Mr. Briney}
\textit{Music: Iki Town (night)}\\
As the party follows the road along Yam Lake, about an hour away from their destination they will run across a humble cottage on the lakeshore, with smoke coming out of the chimney. If they investigate, they will meet a very distressed \linkto{people:mrbriney}, who will inform the party that he lost his most valuable possession to bandits a couple weeks ago: \linkto{items:peeko}. If the party returns the statuette to him, he will be overwhelmed with gratitude, and offer two rewards:
\begin{itemize}
\item A \textit{bag of holding}, which was his wife's but now he doesn't have much need for it
\item The ability to ferry the party anywhere his boat can reach, which is anywhere on Yam Lake, Ylisstol, and any harbor on the eastern coast of Archanea (including the small islands).
\end{itemize}
If the party tells them about their destination, he will be shocked and tell them that that place is a deathtrap, wondering if they are the victims of some practical joke.
\subsection{The Tower}
\textit{Music: Malie City (night)}\\
The abandoned fort is an appropriate distance away that the party will return to Losokyo as night falls (to allow for Turnabout Sisters), this is likely 3 or 4 hours away, to the north. The tower actually belongs to Redd White, and looks like the temple to Odin in Age of Mythology: a five-story tall stone silo surrounded by a wall. The tower contains
\begin{itemize}
\item 3 Priests, the leaders \textit{pro tempore}
\item 4 Acolytes
\item 6 Cultists
\end{itemize}
These are the underlings of White who are maintaining the tower while he is away. In general, these people will spend the day performing temple duties in the courtyard, however at night they retire to the first floor of the tower. They will have been alerted to the party's approach, and will attempt to ambush them when they enter the courtyard, which will be aided by the sealing amulet. \\
\\
The floors of the tower all have a similar structure: circular rooms about 50 feet in diameter.
\begin{enumerate}
\item Ground floor, quarters for cultists and acolytes
Open floorplan, with 20 bunk beds\footnote{adjust to match number of cultists and acolytes} arranged along the wall. The center contains wardrobes with clothing and personal effects of the residents, amounting to about 2d10 gold in total. In the very center, a spiral staircase to the second floor.

\item Second floor, miscellaneous storage for the cultists and acolytes
Plenty of barrels and chests on this floor, containing 
\begin{itemize}
\item 15 barrels of flour
\item 3 barrels of wheat seeds
\item 2 chests of incense (100G)
\item 2 barrels of rations (30 days)
\end{itemize}
The continuation of the staircase going up is blocked off with a locked trap door (15 DC pick, 10 DC break, 3 HP), with ``DO NOT ENTER'' written in Common.
\item Third floor, guard room
The spiral staircase ends on this floor, which is mostly open, with a room on one side of the floor. Between the staircase and the room sits a \textit{Stone Golem}, instructed to kill anyone who enters the room, other than the Master. The Golem is also the key to opening the iron door to the room (no keyhole, 28 DC break, 60 HP, 10 hardness), TBD. The room itself is also trapped, allowing it to take lair actions (initiative 20, loses ties), that emanate from pillars in the room and affect a 10 foot radius. These effects are random, decided by a d4, although the same effect cannot occur twice in a row.
\begin{itemize}
\item Heals the golem 2d10 (only if nearby)
\item Warding wind
\item Anti-magic field
\item Poison gas (3d8 damage, DC 15 constitution save)
\end{itemize}
\item Fourth floor, treasure room
\item Fifth floor, White's workshop
\end{enumerate}