\section{Battle of Fort Sierra}

Two years after the start of the Crusade, in 65 Mostyn (Naga 992), the Ylisseans managed to push through the border mountain range but have not made much more progress. Failing to secure a foothold on the Plegian coast, supplies are forced through the narrow Border Pass that is defended on either side with a sturdy fort. During these years, Fort Sierra on the Ylissean side has seen little action, and the attrition on the front has led to understaffing of Fort Sierra, leaving it with just enough guards to fully man the defensive ballistas and a single captain, \linkto{people:lari}. After raising the issue several times, Lari succeeds in convincing her superiors that the fort needs some officers, a request forwarded to Exalt Mostyn who provided \linkto{people:vill}, \linkto{people:peter}, and \linkto{people:philby}. \\
\\
Lari meets the new officers at the gate and offers to give them a tour of the facility. The fort has 25 foot walls with crenellations (three-quarters cover). Afterwards, she dismisses the officers and returns to her office, inviting the officers to come speak with her once they have settled in. A short while later, it is noticed that a section of the forest is an illusion, possibly hiding the movement of enemies. The fort goes into high alert, as the guards close the gates and prepare the ballistas. Shortly later, a band of 2d4 orcs and 2d4 thugs emerge from the trees near the main gate, prompting Lari to tell Vill and Peter to prepare for defense and Kim to tend to the rear gate, keeping an eye out for a surprise attack from behind. Once Kim is in position, the main band attacks, with orcs charging the gate and thugs providing covering fire, attempting to either take out a ballista or one of the officers. If Vill engages on the ground, the thugs will stop their ranged attacks to focus Vill in melee range.\\
\\
After the first or second round of combat, a large swarm of 4d4 orcs and 4d4 thugs emerge from the forest on the backside of the fort. In response to this, Lari moves to the rear of the fort and begins casting spells (primarily \textit{Fireball}) to aid in the defense of the fort. When Kim succeeds in lowering the gate, Lari will attempt to re-seal it through \textit{Wall of Water} and \textit{Ice Knife}, if possible. In the confusion, Lari will allow Kim to approach, and once in close range will only cast \textit{Frostbite}\footnote{She is scripted to die, so only burn sorcerer points if her death is inevitable}. 