\section{What Happened}

\subsection{Naga 1012}
\subsubsection{Ket 21 - Pentek}

The party met up with Lana Skye just inside the city gates, who proceeded to show them to their accomodations. While entering the hotel room around 2pm, two of the party members (Broderick and San Juro) notice Larry Butz walking out of the hotel. In the room, Lana stood out on the balcony of their hotel room as the party settled down. After a short while, the party goes to the nearby Borscht Bowl Club for lunch, and then Thora asks to see the Police Station. Upon arrival, however, San is promptly arrested for murder. Lana, being only able to vouch for Thora, as she was on the balcony, steps aside, however the party manages to convince Detective Gumshoe to place San under house arrest. Thora, upset, returns to the Borscht Bowl Club and doesn't return. Through some investigation, the rest of the party manages to learn that the victim was Cindy Stone, who just returned from Babahl, and was killed with a small statue. However, with time running out and Mia nowhere in sight, Aleneth, Broderick, and Klob agree to defend San in court. About an hour later, Mia arrives with an autopsy report and tells the party to meet her at the courthouse by 9 AM. 

\subsubsection{Ket 22 - Sombat}
The next morning, the party awakens and finds that the officers that were previously guarding the hotel had left. Seeing an opportunity, San Juro decides to try and escape by descending a rope from the balcony of their room, however Klob tries to stop him by pulling the rope up. San outpaces Klob and jumps to the ground, but fails the landing. Klob then descends the rope and tries to pounce onto San, but also fails; however he quickly charges and tackles San. Broderick eventually notices the scuffle and walks over, and San agrees to go to the courthouse. Upon arrival, the group discovers that the defendant was changed last night, and they had accidentally signed a form agreeing to be the assigned defense team, not the defense team for San Juro. The defendant is Larry Butz, an old friend of San's. In the courtroom, the group manages to poke holes in the witness, Frank Sahwit, testimony, and with some help from Mia manage to break him and uncover his guilt.

In celebration, Mia took the party to the Borscht Bowl Club, and explained that one of the current problems is a tenacious band of bandits that has been terrorizing the town. She tells them of a journalist who seems to have found evidence of their location, and directs the party to talk to her, as she is probably by Yam Lake. Sure enough, the party finds Lotta Hart mid-search for Pasquatch, and she gives them a picture she took up near the Eagle River cliffside of some wagon tracks leading straight to the edge of the cliff. Convinced, the party decides to investigate the area, immediately heading out of the city, stopping to buy a horse on the way out. They set up camp near the main intersection outside the South gate, and train the horse to not be afraid of battle sounds.

\subsubsection{Ket 23 - Vasarnap}
The party wakes up at the crack of dawn and continues towards the Mountains, having to cross a draw bridge over the Yam river. Deep in the forest, a pack of wolves attacks the party, but with the help of Norric, they manage to fight them off. Norric mentions that he's never seen the wolves so aggressive before. The road leads them to Dusky Bridge, which is heavily in disrepair, and an open area with some paths leading further up the mountain. They inspect the near cliffside, and notice an opening to a cavern. Tying a rope to a tree and letting the rope down the cliff-face, they succeed in entering the cavern, and sneak towards the Statue Room. While investigating, Norric uses a produced flame to closely inspect the orb in the center, which causes it to start glowing and a flame to appear on the Primidux and shield statues. After some more investigation, the party moves the statues into an order so that the message on the wall is reproduced in counterclockwise order, revealing a door underneath the message. Satisfied, the party decides to take a short rest before continuing through the door.

On doing so, the party decides to split up and investigate both hallways. Klob and Broderick hide behind the bend of the right passageway, listening to the steps of the patrolling bandit. Once the bandit is near, Klob swiftly grabbed him and threw him to the ground, he and Broderick covering his mouth as Broderick knocked him out. Shortly afterwards, San Juro attempted to kick in the door, however he failed to notice the door opens towards him\footnote{Attack roll of 5} and kicked near the hinges. This thump alerted the thugs inside, as two of them prepared to ambush any intruders and the third goes to alert Stella. Scrambling to figure out how to progress after this, Broderick continues watching down the main hallway and sees a bandit emerge from a side chamber and into the room at the end of the hall, and unknown to the party the thugs in the room leave to take position in the main chamber. The party then bursts into the now-empty meeting room, noticing some sound coming from the stairway and the door to the great hall, which was left slightly ajar. After no discussion whatsoever, San Juro (successfully) kicked open the door and began firing at the thugs and at Stella, Klob rushed in to strike a thug, and the others began landing attacks as well. However, as Klob rushed too far, Norric and San Juro were cut off by one of the thugs, and Broderick had to go upstairs to deal with the bandits on the second story. 

After a tough fight, the party manages to take down all but Stella and a singular bandit, however Stella fells the entire party (the bandit taking down San Juro) but Norric, whom she gives an offer to spare him and his companions should they agree to join her bandit party. He agrees, and while Norric heals Broderick and stabilizes Klob, Stella goes upstairs to stabilize and retrieve San Juro. Norric and Broderick discuss the terms of the arrangement, convincing Stella to revive Klob and San Juro, although in handcuffs. Klob goes into a long-winded talk about the naming of Yam lake, and while he does so, Broderick helps San Juro repair his jammed gun. Training a shot, he fires at Stella, and the combined attacks of the four party members force her to surrender.

After talking to her, the party loots the hideout and ties up Stella and the six surviving bandits. 

(Next session)
The party interrogates Stella, who tells them that she did not know of the other entrance into the Hideout and that she does not know who provided her with the directions. The group retrieved several items from the cave, including a Ring of Water Walking, a Cloak of Protection, \linkto{items:peeko}, and studded leather armor, and also a book detailing the bandits' heists, going back until Neige of the previous year (5 months ago). During the interrogation, however, Stella attempted to get the attention of the remaining bandit, who was in the process of tending to his unconscious comrades. Broderick and Norric chased after him into the sleeping quarters and handcuffed him. They thus discovered the existence of a separate entrance below the cave, which connected a room filled with rubble to a riverbank though a rather craggy opening. On the riverbank was a ship, and the party attempted to shanghai the bandits into manning the ship for them, to no avail, despite hanging one bandit overboard. They did manage to convince one bandit, Alm, to give some advice, and for this he was cut free from the other bandits (who were all tied together), and the party set sail onto Yam Lake with six bandits and Stella in tow. 

Partway through the voyage back to Losokyo, the bandits stage a minor uprising, where they convinced the captain (San Juro) to turn the ship and cause the sail to catch the wind and swing across the deck, knocking Norric into Klob. With this opportunity, two of the bandits are able to jump and rip a large hole in the bottom of the sail. Outraged, San Juro immediately shoots and kills two of the bandits, and Klob throws the remaining ones overboard, effectively drowning them, and leaving Alm alive. As Norric noticed an oncoming storm, the party hugged the eastern coast of the lake, eventually making camp as the storm arrived. 

\subsubsection{Ket 24 - Honapon}
As the party broke camp, they interrogated Stella some more and discovered that her son, Fekete, is being used to coerce Stella into being a bandit, and he will be killed if an anonymous They finds out she has revealed this. For this reason, she refuses to even cross the bridge over the Yam river, forcing Broderick to run to Losokyo to fetch Aleneth to aid in the interrogation. While he is gone, Alm breaks out of his bonds and grapples San Juro, allowing Stella to run away. Klob keeps pace for a while, but can't keep up with her. Norric, on the other hand, transforms into a wolf and is able to track her, following her all the way back to the lake. However, he is too late, as Stella picked up a large rock on the shore and drowned herself, rather than be forced to endanger her son. As Broderick and Aleneth return, they all talk with Alm for a short while and learn that he was forced into banditry after an accidental death in his past. After a funeral for Stella, they allow Alm to escape on a promise he follow a better path.

Upon returning to the city, the party meets up with Mia, who congratulates them and immediately recommends they talk to the Mayor. After a short wait, the party has an audience with Mayor Al Calder and four other councilmen, who inquire heavily into the conditions of the bandit hideout and are moderately disappointed with the lack of investigation done by the group. During this questioning, the party almost reveals that they murdered several of the bandits after the conflict had taken place, but the council neglected to probe further. The meeting ends with the party receiving great thanks from the Mayor on behalf of the city.

Following the meeting, Mia recommends several locations for the party to explore, and particularly recommends that they see a Troupe Gramarye magic show, which they do. Aleneth sneaks off from the group to investigate the magic shop Rinea, which was owned by a man who was found dead on the banks of the Yam river a few months prior, but finds a new magic shop, Gollyths, in its place. At the Sunshine Colliseum, Norric is approached by Thalassa Gramarye, who asks him to be a volunteer at the start of the show. He agrees, but secretly arranges for Aleneth to take his place. Right before the show begins, Aleneth, disguised as Norric, and Norric, wild shaped into a squirrel, are brought to the dressing room to meet the Gramaryes. In order to be useful, Aleneth needs to drop all enchantments and remove all magical items, which he does (revealing that the Norric exterior was an illusion), but asks for a mask. Shortly after the show begins, Magnifi notes that the magic show would not be nearly as interesting if there were arcane tricks afoot, and so to demonstrate the effectiveness of the arcane detectors, he asks Aleneth to come onstage and perform some magic. Aleneth casts a disguise on himself, and then with prompting from Magnifi, casts an illusion on Magnifi. Magnifi, however, appears to teleport away from the illusion, twice, failing to trip the detectors either time. For his cooperation, Aleneth is given a \linkto{item:detectspade}, and the ability for the party to talk to the Gramaryes after the show.

\subsubsection{Ket 25 - Neiged}
Waking up early, Norric went over to People Park to meditate and talk to some animals. After returning, the party decided to head to Ivy University to talk to Arcadia. Arcadia meets them happily and shows them around the library. The party investigates the suicides in several ways:
\begin{itemize}
\item Klob gathered some newspapers from six months ago, but got caught up in actually reading the newspapers that, while learning a lot of what happened between Eb 4 and 10, did not actually learn anything immediately relevant, however he did learn about the creation of a special investigative unit for the SL-9 incident, this year's World Faire theme is ``housecleaning'', and that there was some tragedy at a hospital in Ylisstol.
\item Broderick read a case study of murders and suicides in Losokyo, learning about the DL-6 Incident, the faked suicide of Sophie (Dahlia Hawthorne), and another incident of where a woman was charged with hanging her husband, but was found not guilty after her lawyer proved that it was a suicide, as well as alleged fraudulent evidence against the prosecution.
\item San Juro talked to Professor Binns about the history of bandit activity in Ylisse, and learned that it mostly rose with Exalt Emmeryn's reduction of the Ylissean army. He mentioned, however, that the Losokyan bandits were very good at their jobs
\item Norric read about the Eagle Mountains and the surrounding forest, in particular reading a story about a boy named Inigo who was raised by Mogelbaum.
\item Aleneth switched between reading newspapers and thinking about the apocalypse, achieving little on either front
\end{itemize}
Afterwards, Arcadia brought them to the Arcane Institute, where she introduced them to Dwayne, a research student there. He explained the history of the Arcane Institute, and as friends of Mia, gave them a prototype of a 3-1 Sender Block. Eventually the party asked about Rinea, and Dwayne encouraged the party investigate around the Lordly Tailor.

The party split into two, with Norric and Aleneth entering the Lordly Tailor and Broderick and San Juro going to Gollyths. At the Lordly Tailor, the group learned that Rinea still walks along the nearby canal in the evenings, and also Norric bought some boots and rope. At Gollyths, Broderick and San Juro learn that the shopkeeper has an affinity for gardening supplies, but also that Broderick's ring of water walking is elven-made, from southern Ylisse, and that San's seagull figurine is not artisan-made. They confirm that Halcyon's magical items were of high quality, with a cat motif. 

Deciding to wait until dusk to talk to Rinea, the party gave Mia a visit to ask about the SL-9 incident. She doesn't have much to say, except that Lana is likely very busy right now, although they could try to arrange a meeting. She doubted that Halcyon's suicide had much to do with the SL-9 incident, but encouraged them to talk to Lana. The party went over to the Criminal Affairs Department visitors' entrance and talked to Detective Bruce, who informed them that Lana was very busy, but they will let the party know when a meeting can be arranged. Additionally, Officer Meekins would be available tomorrow to let them review old case files.

This having taken some time, the party split, with San and Broderick returning to the hotel room to practice catching bullets (inspired from the previous day's Quick Draw Shoot'em). After a few failed attempts, success, and Broderick caught a bullet, although bruising his hand in the process. Meanwhile, Klob, Norric (disguised), and Aleneth returned to Tailor Park to meet with Rinea, who was gardening in the park at the time. She tells them about how she felt unsatisfied by the police investigation, and turned to BlueCorp for additional investigation. However, they told her that it was likely just stress from the shop. However, Rinea is unsatisfied by this answer, as even though Halcyon had become withdrawn over the previous five years, she felt like times weren't as bad as the first two years of running the shop, when the shop almost failed and their cat ran away. In any case, the party members decide to investigate BlueCorp some more. 

Upon returning to the hotel, Klob attunes to the Sender Block and gives Mia a call at 9pm. Annoyed, Mia tells him that she might have some info at the office, but she will look into the general perception of BlueCorp. Afterward, the party travelled to BlueCorp, where they were met predictably with a locked door, and so decided to retire to a nearby bar.